% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2022 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).

%%
%% Command line arguments table.
%%
\small
\begin{longtable}[h] {>{\raggedright\small}m{1.1in}|>{\raggedright\small}m{2in}|>{\raggedright\small}m{1.5in}|>{\raggedright\let\\\tabularnewline\small}m{1in}}
  \caption{List of \Xyce{} command line arguments.} \label{cmd_line_arg_list} \\ \hline
  \rowcolor{XyceDarkBlue}{\color{white}\bf Argument} &
  \color{white}\bf Description &
  \color{white}\bf Usage &
  \color{white}\bf Default \\ \hline \endfirsthead
  \caption[]{List of \Xyce{} command line arguments.} \\ \hline
  \rowcolor{XyceDarkBlue}{\color{white}\bf Argument} &
  \color{white}\bf Description &
  \color{white}\bf Usage &
  \color{white}\bf Default \\ \hline \endhead

-h &
Help option. Prints usage and exits. &
\verb+-h+ &
- \\ \hline

-v &
Prints the version banner and exits. &
\verb+-v+ &
- \\ \hline

-license &
Prints the license text and exits. &
\verb+-license+ &
- \\ \hline

-capabilities &
Prints a list of compiled-in options and exits. &
\verb+-capabilities+ &
- \\ \hline

-delim &
Set the output file field delimiter. &
%% have to break line to keep table neat
\verb+-delim+
\verb+<TAB|COMMA|string>+ &
- \\ \hline

-o &
Place the output result(s) into file(s) with the specified basename
and the appropriate extension (e.g., \verb+<basename>.prn+ or 
\verb+<basename>.mt0+). &
\verb+-o  <basename>+ &
output file name(s) based on netlist file name. \\ \hline

-l &
Place the log output into specified file. &
\verb+-l  <file>+ &
Log output sent to standard out. \\ \hline

-r &
Output a binary rawfile. &
\verb+-r  <file>+ &
No rawfile written. \\ \hline

-a &
Use with \verb+-r+ to output a readable (ASCII) rawfile.
Without the concurrent use of \verb+-r+, \verb+-a+
will cause all .PRINT lines that use FORMAT=RAW to produce
ASCII rawfiles. &
\verb+-r  <file> -a+

\verb+-a+ &
Default rawfile is binary. \\ \hline

-nox &
Use the NOX nonlinear solver. &
\verb+-nox  <ON|OFF>+ &
on \\ \hline

-linsolv &
Set the linear solver. &
%% have to break line to keep table neat
\verb+-linsolv+
\verb+<KLU|+
\verb+KSPARSE|SUPERLU|+
\verb+AZTECOO|BELOS>+ &
klu(serial) and aztecoo(parallel) \\ \hline

-param &
Print a terse summary of model parameters, device parameters and default values. &
\verb+-param+ &
- \\ \hline

-remeasure &
Recompute .measure and/or .fft results with existing data. &
\verb+-remeasure+ &
- \\ \hline

-syntax &
Check netlist syntax and exit.&
\verb+-syntax+ &
- \\ \hline

-norun &
Check netlist syntax and topology and exit. &
\verb+-norun+ &
- \\ \hline

-quiet &
Suppress some of the simulation-progress messages
sent to stdout for transient simulations. &
\verb+-quiet+ &
- \\ \hline

-namesfile &
Output a list of all solution variables generated by the netlist
into \tt{<filename>} &
%% have to break line to keep table neat
\verb+-namesfile+
\verb+<filename>+ &
- \\ \hline

-noise\_names\_file &
Output a list of all noise sources for all devices generated by the netlist
into \tt{<filename>} &
%% have to break line to keep table neat
\verb+-noise_names_file+
\verb+<filename>+ &
- \\ \hline

-randseed &
Set random number seed for expression library's random number functions
 and also \texttt{.SAMPLING} analysis. &
\verb+-randseed <number>+ &
If not provided, Xyce will select a seed using the system ``time'' function.  \\ \hline

-maxord &
Maximum time integration order. &
\verb+-maxord <1..5>+ &
- \\ \hline

-jacobian\_test &
Jacobian matrix diagnostic. &
\verb+-jacobian_test+ &
- \\ \hline

-redefined\_params & 
Set precendence for multiply defined parameters. Can be set to \texttt{ignore} (use last), \texttt{usefirst}, \texttt{warn} or \texttt{error}. &
\verb+-redefined_params+
\verb+<option>+ & \texttt{ignore}, which means use the last duplicate parameter in the netlist without warning or error.
  \\ \hline

-hspice-ext &
Hspice parser extensions.  This will override several parser issues that are difficult to translate with scripts. 

&
\verb+-hspice-ext+
\verb+<all|separator+
\verb+|units|math>+ & 
The second argument will determine which features are enabled.  
For details see the \Xyce{} Reference Guide\ReferenceGuide{}.
\\ \hline


\end{longtable}

