% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2022 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).

% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2022 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


%%
%% Changes to Xyce input since the last release.
%%
{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\textbf{Change} &
  \color{white}\textbf{Detail} \\ \hline \endfirsthead
  \caption[]{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\textbf{Change} &
  \color{white}\textbf{Detail} \\ \hline \endhead

Change in output file names produced by \texttt{.FOUR} analyses &
Results from Fourier analyses are now output to \texttt{<netlistName>.four\#} files,
where the suffixed number (\texttt{\#}) starts at \texttt{0} and increases for multiple
iterations (\texttt{.STEP} iterations) of a given simulation. \\ \hline

Changes in the format of \texttt{.FFT} output sent to the
\texttt{<netlistName>.fft\#} files  & The output in those
files is no longer filtered based on the \texttt{FREQ}, \texttt{FMIN} and
\texttt{FMAX} values on each \texttt{.FFT} line.  Instead the data for
every harmonic is output.  The \texttt{START} and \texttt{STOP} values
used for each \texttt{.FFT} analysis are now output. \\ \hline

Additional \texttt{.FFT} output to stdout & If \texttt{.OPTION FFT FFTOUT}
is set to 1 then the additional metrics (ENOB, SFDR, SNR, SNDR and THD)
and a sorted list of the 30 largest harmonics, for each \texttt{.FFT} line,
are now output to stdout. \\ \hline

Changes to output file names produced by the -o command line option &
In prior releases, the -o filename only applied to the file name
produced by the primary \texttt{.PRINT} line.  The -o filename is now
used as the ``basename'' for all of the output files. As an example,
for a \texttt{.TRAN} analysis, this command line will now produce the
output file \verb+<results>.prn+, instead of the file \verb+<results>+,
from the \texttt{.PRINT} line.
\begin{vquote}
   Xyce -o results <netlistName>
\end{vquote}

The results from any \texttt{.MEASURE TRAN}, \texttt{.MEASURE TRAN\_CONT},
\texttt{.FFT} and/or \texttt{.FOUR} lines in the netlist will now be placed into
the files \verb+<results>.mt0+, \verb+<results>_measurename.mt0+,
\verb+<results>.fft0+, and \verb+<results>.four0+, respectively.  For a
\texttt{.STEP} analysis, the results file \verb+<results>.res+ will also be
made.

\\ \hline

\end{longtable}
}
