% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2019 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).



%%
%% Known defects and workarounds.
%%
%% This section should highlight significant defects that were not fixed in
%% the release

{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Known Defects and Workarounds.} \\ \hline
  \rowcolor{XyceDarkBlue} \color{white}\bf Defect & \color{white}\bf Description
  \\ \hline \endfirsthead
  \caption[]{Known Defects and Workarounds.} \\ \hline
  \rowcolor{XyceDarkBlue} \color{white}\bf Defect & \color{white}\bf Description
  \\ \hline \endhead
% EXAMPLE:
%\textbf{bug number-SRN}: bug title & Description of KNOWN BUG THAT HAS NOT BEEN
  %FIXED.

%\textbf{\textit{Workaround}}: Describe how to work around this bug.
%\\ \hline
%
%  

\textbf{838-SON}: Shared library plugins do not work in parallel &  While binaries of \Xyce{} are not distributed supporting this capability, is possible to build \Xyce{} from source using options to allow it to load device models as shared library plugins.  It has been discovered that this capability does not work correctly in parallel.  There is currently no workaround, and the issue was discovered too late to fix it for Release 6.6.  In Release 6.6, it is only possible to use shared library plugins in serial builds, or in single-processor runs of parallel builds.
\\ \hline

\textbf{833-SON}: Incorrect error message when requesting power for unsupported 
devices (K, O, U and some Y devices) &  Netlist parsing will fail and produce 
an error message if power (\texttt{P()} or \texttt{W()}) is requested for a device
that does not support power.  However, for example for device \texttt{K1}, those 
error messages will reference \texttt{I(K1)} rather than \texttt{P(K1)} or 
\texttt{P(K1)}. \\ \hline

\textbf{819-SON}: Transient sensitivity analysis output is not interpolated when used with .options timeint output\_interval &

  Normally, any transient output is automatically interpolated if the user requests outputs at specific times.  The adjoint sensitivity calculation does not do this, and will simply output sensitivities from the time point nearest the requested one.
 
\textbf{\textit{Workaround}}: In general, transient adjoint sensitivity calculations are not efficient when applied to entire waveforms, so in practice this isn't the best way to get transient sensitivities for specific time points.  A better way to get sensitivities from specific time points is to use the \texttt{.options sensitivity adjointTimePoints} parameter, which allows the user to specify a list of specific time points at which to compute sensitivities.
  \\ \hline

\textbf{812-SON}: Undocumented limitations on, and bugs with, parameter and global 
parameter names & Based on external customer input and pre-release testing, there are
some bugs and undocumented limitations on parameter and global parameter names in 
\Xyce{}. Parameters and global parameters should start with a letter, rather than with a
number or ``special'' character like \#.  In addition, the use of a single 
character $V$ as a global parameter name can result in either netlist parsing failures
or incorrect results from \texttt{.PRINT} lines.  \\ \hline

\textbf{807-SON}: BSIM4 convergence problems with non-zero rgatemod value &
There have been reports of convergence problems (e.g., the \Xyce{} simulation
fails part way through and says that the ``time step is too small'')  when the 
\texttt{rgatemod} parameter is non-zero. \\ \hline

\textbf{805-SON}: Parser fails to collect linear mutual inductors in an include file & 
\Xyce{} will fail to collect component inductors together, into a mutual inductor, when
they are in an include file rather than in the top-level netlist file.  
\textbf{\textit{Workaround}}: Move the relevant L and K device statements into 
the top-level circuit. \\ \hline

\textbf{794-SON}: Bug in TABLE Form of \Xyce{} Controlled Sources & In some cases, a \Xyce{}
netlist with a controlled source, that uses the TABLE form, will get the correct answer 
at first.  However, it may then "stall" (e.g., keep taking really small time-steps)
and never complete the simulation run.  

\textbf{\textit{Workaround}}: In some cases, the TABLE specification for the controlled
source can be replaced with a Piecewise Linear (PWL) source that uses nested IF 
statements. \\ \hline

\textbf{785-SON}: \Xyce{} hangs in parallel when passed a directory rather than a file &
This bug is related to SON Bug 730 (``\Xyce{} hangs when passed a directory instead of a 
netlist ''), which was fixed in version 6.5 of \Xyce{}.  Further testing has shown that \Xyce{}
will hang (during parallel execution) if a directory is used, rather than a file, in
\texttt{.LIB} or \texttt{.INC} statements.  \Xyce{} may also hang in parallel if
the ``output file'' is either a directory or a file in a non-existent directory.
This can happen with either the \texttt{FILE=} keyword on a \texttt{.PRINT} line or
with the \texttt{-o} command line option. \\ \hline

\textbf{783-SON}: Use of ddt in a B-Source definition may produce incorrect results  & The \texttt{DDT()} 
function from the \Xyce{} expression package, which implements a time derivative, may not function 
correctly in a B-Source definition.

\textbf{\textit{Workaround}}: None. \\ \hline

\textbf{727-SON}: \Xyce{} parallel builds hang randomly on OS X & During Sandia's internal 
nightly testing of the OSX parallel builds, we see that \Xyce{} ``hangs on exit'' with an 
estimated frequency of less than 1-in-5000 simulation runs.  We have not seen this issue 
with parallel builds for either RHEL6 or BSD.  The hang is on exit, whether on a successful 
exit or on an error exit.  The hang occurs after all of the \Xyce{} output has occurred though.  
So, the user will get their simulation results, but might have trouble if the individual \Xyce{} runs 
are part of a larger script.

\textbf{\textit{Workaround}}: None. \\ \hline

\textbf{718-SON}: Missing error message for invalid nodes in expressions on .PRINT lines & If an invalid node
is specified on a \Xyce{} \texttt{.PRINT TRAN} line then \Xyce{} should return a fatal error during netlist
parsing (e.g., \texttt{.PRINT TRAN V(BOGONODE)} will produce an error message of \texttt{undefined 
symbol in .PRINT command: node BOGONODE}, if \texttt{BOGONODE} does not exist in the netlist).  However, if the
invalid node is inside a \Xyce{} expression (e.g., \texttt{.PRINT TRAN \{V(BOGONODE)\}}) then \Xyce{} will 
not produce an error message during netlist parsing and the output value for \texttt{\{V(BOGONODE)\}} will 
be zero for all time-steps.

\textbf{\textit{Workaround}}: There is none, other than noticing that a output waveform value is 
unexpectedly all zeroes, and correcting the \texttt{.PRINT} statement. \\ \hline

\textbf{715-SON}: I(*) for subcircuit nodes does not work properly on .PRINT lines & 
\texttt{.PRINT TRAN I(*)} works for nodes at the top-level of the netlist.  However, it will
fail during netlist parsing if there are nodes in subcircuits.  The error message will be 
something like \texttt{Function or variable I(V:X1:1) is not defined}.

\textbf{\textit{Workaround}}: Explicitly put the desired lead or branch currents, using the
fully qualified device names, in the \texttt{.PRINT} statement. \\ \hline

\textbf{707-SON}: Behavior for invalid nodes on .FOUR lines and in .MEASURE statements &
There are issues with \texttt{.FOUR} lines and \texttt{.MEASURE} statements that accidentally
use node names that are not in the netlist.  In that case, the \texttt{.cir.four} output file 
will contain a mix of all zeros and meaningless values (e.g., NaN), and \Xyce{} will not produce a warning or error 
message about the invalid node names.  Similarly, the measure statement will run without a 
warning message about the invalid node names.  The measure result will then be zero, rather than 
FAILED. \\ \hline

\textbf{661-SON} Branch Currents and Power Accessors (I(), P() and W()) Do Not Work 
Properly in .RESULT Statements  & There are two issues.  First, \texttt{.RESULT} statements 
will fail netlist parsing if the requested branch current is omitted from the \texttt{.PRINT TRAN} 
line.  As an example, this statement (\texttt{.RESULT I(R1)}) requires either \texttt{I(R1)},
\texttt{P(R1)} or \texttt{W(R1)} to be on the \texttt{.PRINT TRAN} line.  Second, the
output value, in the \texttt{.res} file, for the lead current or power calculation will 
always be zero.
\\ \hline 

\textbf{652-SON}: HB output is buggy & While a straightforward use of \texttt{.print HB} works as described in the \Xyce{} Users and Reference Guides, several of the documented features do not work as intended.

\texttt{.print HB\_FD} and \texttt{.print HB\_TD} are intended as a way of specifying variable lists for frequency- and time-domain outputs, respectively.  It has been discovered that these only produce output if there are print specifications for {\em both\/} frequency and time domain.  That is, if only one of \texttt{.print HB\_FD} or \texttt{.print HB\_TD} is present in the netlist, no output will be produced at all.   

\textbf{\textit{Workaround}}: When performing harmonic balance analysis, always specify enough print lines so that both time- and frequency-domain variables are output.  This could be by specifing \texttt{.print HB} alone, by specifying both \texttt{.print HB} and \texttt{.print HB\_TD}, or by specifying both \texttt{.print HB\_FD} and \texttt{.print HB\_TD}.
\\ \hline


\textbf{583-SON}: Switch with RON=0 leads to convergence failure. &  The switch device does not prevent a user from specifying \texttt{RON=0} in its model, but then takes the inverse of this value to get the ``on'' conductance.  The resulting invalid division will either lead to a division by zero error on platforms that throw such errors, or produce a conductance with ``Not A Number'' or ``Infinity'' as value.  This will lead to a convergence failure.

\textbf{\textit{Workaround}}: Do not specify an identically zero resistance for the switch's ``on'' value.  A small value of resistance such as 1e-15 or smaller will generally work well as a substitute. \\ \hline


\textbf{469-SON}: Belos memory consumption on FreeBSD and excessive CPU on other
platforms &
Memory or thread bloat can result when using multithreaded dense linear algebra
libraries, which are employed by Belos.  If this situation is observed, either build
\Xyce{} with a serial dense linear algebra library or use environment variables to control
the number of spawned threads in a multithreaded library.
\\ \hline


\textbf{468-SON}: It should be legal to have two model cards with the same model
name, but different model types. & SPICE3F5 and ngspice only require that
model cards of the same type have unique model names. They accept model cards
of different types with the same name.  \Xyce{} requires that all model card names be unique.
\\ \hline


\textbf{250-SON}: NODESET in \Xyce{} is not equivalent to NODESET in SPICE & As
currently implemented, \texttt{.NODESET} applies the initial conditions given throughout
a full nonlinear solve for the operating point, then uses the result as an
initial guess for a second nonlinear solve with no constraints.  This is not
the same as SPICE, which merely applies the given initial conditions to a
single nonlinear solve for the first two iterations, then lets the problem
converge with no further constraints.  This can lead to \texttt{.NODESET} failing in \Xyce{}
where the same netlist in SPICE might not, if the initial conditions are such
that a full nonlinear solve cannot converge with those constraints in place.
There is no workaround.
\\ \hline

\textbf{247-SON}: Expressions don't work on .options lines & Expressions enclosed
in braces (\{ \}) are handled specially throughout \Xyce{}, and may only be used
in certain contexts such as in device model or instance parameters or on
\texttt{.PRINT} lines.
\\ \hline


\textbf{49-SON} \Xyce{} BSIM models recognize the model TNOM, but not the
instance TNOM & Some simulators allow the model parameter TNOM of BSIM devices to be specified on the instance line, overriding the model parameter TNOM.  \Xyce{} does not support this.
\\ \hline

\textbf{37-SON}: Connectivity checking is broken for devices with more than 10
leads & The diagnostic code used by the \Xyce{} setup that checks circuit
topology for basic errors such as a node having no DC path to ground or a node
being connected to only one device has a bug in it that causes the code to emit
a cryptic error message, after which the code will exit.  This error has so far
only been seen when a user has attempted to connect a large number of inductors
together using multiple mutual inductor lines.  The maximum number of
non-ground leads that can be used without confusing this piece of code is 10.
If your circuit has that type of large, highly-connected mutual inductor and
the code exits with an error message, this bug may be the source of the problem.

The error message now includes a recommendation to use the workaround below.

\textbf{\textit{Workaround}}: Disable connectivity checking by adding the line

\begin{alltt} .OPTIONS TOPOLOGY CHECK_CONNECTIVITY=0 \end{alltt}

to your netlist.  This will disable the check for the basic errors such as
floating nodes and improperly connected devices, but will allow the netlist to
run with a highly-connected mutual inductor.
\\ \hline


\textbf{27-SON}: Fix handling of .options parameters & When specifying .options
  for a particular package, what gets applied as the non-specified default
  options might change.  \\ \hline

\textbf{1962-SRN}: Voltages from interface nodes for subcircuits may not work
correctly in expressions on \texttt{.PRINT} lines & An expression that uses a 
voltage from an interface node to a subcircuit on a \texttt{.PRINT} line 
may only work if that voltage node is also used outside of the expression on 
the \texttt{.PRINT} line.  A simple example is as follows.  The expression 
\texttt{\{V(X1:a)*I(X1:R1)\}} prints out as 0, unless \texttt{V(X1:a)} is also on 
the \texttt{.PRINT} line.
\\ \hline

\textbf{1923-SRN}: LC lines run out of memory, even if equivalent (larger) RLC
lines do not. &  In some cases, circuits that run fine using an RLC approximation for a
transmission line, exit with an out-of-memory error if the (supposedly smaller) LC
approximation is used.
\\ \hline

\textbf{1903-SRN}: \Xyce{} fails to collect several inductors into a linear mutual inductor &
In some rare cases with complex include file usage, the mutual inductor syntax with multiple couplings can fail to work. \Xyce{} will return an error message that it can not find 
\texttt{L\_L1}:
{\tt
\begin{verbatim}
L_L1         node1 node1 inductance1
L_L2         node3 node4  inductance2
L_L3         node5  node6  inductance3
L_L4         node7 node8  inductance4
K_K1         L_L1 L_L2 L_L3 L_L4   .999 
\end{verbatim}
}

\\ \hline

\textbf{1595-SRN}: \Xyce{} won't allow access to inductors within subcircuits for
mutual inductors external to subcircuits & It is not possible to have a mutual
inductor outside of a subcircuit couple to inductors in a subcircuit.

\textbf{\textit{Workaround}}: Put all inductors and mutual inductance lines that couple to
them together at the same level of circuit hierarchy.
\\ \hline

\end{longtable}
}
