% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2019 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).



%%
%% Changes to Xyce input since the last release.
%%
{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endfirsthead
  \caption[]{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endhead

The \texttt{FORMAT=PROBE} and \texttt{FORMAT=RAW} print formats for 
\texttt{.PRINT SENS} output have changed & Those two print formats are 
still unsupported for \texttt{.PRINT SENS} output. However, they now 
default to \texttt{FORMAT=STD} with the file extensions of
``\texttt{.SENS.prn.}'' In earlier versions of \Xyce{}, their format was
\texttt{FORMAT=NOINDEX.} 
\\ \hline

The \texttt{FORMAT=PROBE} and \texttt{FORMAT=RAW} print formats for 
\texttt{.PRINT TRANADJOINT} output have changed & Those two print formats 
are still unsupported for \texttt{.PRINT TRANADJOINT} output. However,
they now default to \texttt{FORMAT=STD} with the file extensions of 
``\texttt{.TRADJ.prn.}'' In earlier versions of \Xyce{}, their format was 
\texttt{FORMAT=NOINDEX}. \\ \hline

The expression package now supports floor and ceil functions & Support
for \texttt{floor} (greatest integer less than or equal to argument)
and \texttt{ceil} (smallest integer greater than or equal to argument)
functions has been added to the expression package, and these
functions may be used anywhere expressions are valid.  Note that
because the functions are discontinuous, use in B source expressions
could lead to timestep-too-small errors in some cases, as documented
in the Users' Guide chapter on ABM guidance. \\ \hline

The allowed syntax for \texttt{.LIB} statements was changed & \Xyce{} 
now rigorously supports the HSPICE .LIB syntax where there is a 
library definition (\texttt{.LIB <library\_name>}) and a 
library inclusion (\texttt{.LIB <library\_file> <library\_name>}).
The use of \texttt{.LIB <name>} as a synonym for
\texttt{.INC <name>} is no longer supported.\\ \hline

A new \texttt{.OPTIONS DIST} category to support parallel distribution options &
There is a new \texttt{.OPTIONS DIST} category to support parallel
distribution options that a user can use to improve the parallel
performance of \Xyce{}.  At this time the only option available is
\texttt{STRATEGY}, which can be used to select the device distribution
strategy being used by \Xyce{}.  The new options are described in the
Users' Guide chapter on ``Guidance for Running Xyce in Parallel''.

\end{longtable}
}
