% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2019 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


%%-------------------------------------------------------------------------
%% Purpose        : Release notes for Xyce version 6.1.
%% Special Notes  : Graphic files (pdf format) work with pdflatex.  
%% Creation Date  : {03/24/2006}
%%-------------------------------------------------------------------------

\documentclass[11pt,report,strict]{SANDreport}
\usepackage[hyperindex=true, colorlinks=false]{hyperref}
\usepackage{makeidx, ltxtable, multirow}
\usepackage{Xyce}
\pdfcatalog {/PageMode /UseNone}

{\renewcommand{\arraystretch}{1.2}

% ---------------------------------------------------------------------------- %
%
% Set the title, author, and date
%
    \title{\XyceTitle{} Parallel Electronic Simulator Release Notes\\Release 6.1}
    \XyceVersion{6.1}

    % There is a "Printed" date on the title page of a SAND report, so
    % the generic \date should generally be empty.
    \date{}

% ---------------------------------------------------------------------------- %
% Set some things we need for SAND reports. These are mandatory
%
%Submitted to R&A 28 Aug 2013 Tracking number 5327111,  approved 29 Aug

\SANDnum{SAND2014-2402}
\SANDprintDate{March 2014}
\author{Eric R. Keiter, 
            Ting Mei, 
            Thomas V. Russo, \\
            Richard L. Schiek, 
            Peter E. Sholander,
            Heidi K. Thornquist,
            Jason C. Verley\\
            Electrical Models and Simulation \\[1ex]
\\
            Sandia National Laboratories\\
            P.O. Box 5800\\
            Albuquerque, NM 87185-1177 \\
\\
\and 
David G. Baur\\
  Raytheon\\
  1300 Eubank Blvd\\
  Albuquerque, NM 87123 \\
}
\SANDauthor{Eric R. Keiter, Ting Mei, Thomas V. Russo, Richard L. Schiek, Peter E. Sholander, Heidi K. Thornquist, Jason C. Verley, David G. Baur}
% ---------------------------------------------------------------------------- %
% Start the document

\begin{document}
\maketitle
%\draft
\begin{abstract}
  The highlights of the \XyceTM\ 6.1 release are documented.
\end{abstract}
\cleardoublepage
\tableofcontents


% ---------------------------------------------------------------------- %
% This is where the body of the report begins; usually with an Introduction
%
\SANDmain		% Start the main part of the report
\section{Scope/Product Definition}

The \Xyce{} Parallel Electronic Simulator has been written to support, in a
rigorous manner, the simulation needs of the Sandia National Laboratories
electrical designers.  Specific requirements include, among others, the
ability to solve extremely large circuit problems by supporting large-scale
parallel computing platforms, improved numerical performance and
object-oriented code design and implementation.

The \Xyce{} release notes describe:
\begin{XyceItemize}
  \item Hardware and software requirements
  \item New features and enhancements
  \item Any defects fixed since the last release
  \item Current known defects and defect workarounds
  \item Incompatibilities With Other Circuit Simulators
\end{XyceItemize}

For up-to-date information not available at the time these notes 
were produced, please visit the \Xyce{} web page at 
{\color{XyceDeepRed}\url{http://xyce.sandia.gov/}}.


\section{Hardware/Software}
This section gives basic information on supported platforms and hardware
and software requirements for running \Xyce{} 6.1.

\subsection{Supported Platforms (Certified Support)}
\Xyce\ 6.1 currently supports any of the following operating system platforms
(all versions imply the earliest supported---\Xyce{} generally works on later
versions as well).  These platforms are supported in the sense that they have
been subject to certification testing for the \Xyce{} version 6.1 release.  

\begin{XyceItemize}
\item Red Hat Enterprise Linux${}^{\mbox{\textregistered}}$ 5, x86 (serial only) and x86-64 (serial and parallel)
\item Red Hat Enterprise Linux${}^{\mbox{\textregistered}}$ 6, x86-64 (serial and parallel)
\item Microsoft Windows 7${}^{\mbox{\textregistered}}$, x86 (serial)
\item Apple${}^{\mbox{\textregistered}}$ OS X, x86-64 (serial and parallel)
\item TLCC (serial and parallel)
\item Red Sky (serial and parallel)
\end{XyceItemize}

\subsection{Build Supported Platforms (not Certified)}
The platforms listed in this section are ``not supported'' in the
sense that they are not subject to nightly regression testing, and
they also were not subject to certification testing for the \Xyce{}
version 6.1 release.  Despite this lack of testing rigor, \Xyce{} has
been known to run under these configurations.

\begin{XyceItemize}
\item FreeBSD 9.x on Intel x86 and x86-64 architectures (serial and parallel)
\item Distributions of Linux other than Red Hat Enterprise Linux
\item Microsoft Windows under Cygwin and MinGW.
\end{XyceItemize}

Please contact the Xyce development team for platform and configuration availability.

\subsection{Hardware Requirements}

The \Xyce{} team has not determined a minimum memory or processor
speed requirement.  Any modern computer should have enough memory and
processor power to run moderately sized circuits in serial with
\Xyce{}.  Naturally, memory requirements grow with problem size.  

Running \Xyce{} in parallel will require a system with at least two
processors. For problems of the size where parallel operation is
beneficial (thousands of devices per processor), one can expect to
need several gigabytes of memory per processor. 

For the very largest problems that \Xyce{} can run (millions of
devices), one will require a cluster system with a sufficient number
of nodes to distribute the problem efficiently, and sufficient memory
per node to support the distributed problem.  

\subsection{Software Requirements}
Several libraries are required to run \Xyce{} or build \Xyce{} from source on a
platform.  Serial versions of the \Xyce{} binary have no run-time software
requirements, as they ship with all the shared libraries they need.  However,
parallel versions require Open MPI
({\color{XyceDeepRed}\url{http://www.open-mpi.org/}}) (version 1.4 or higher)
at run time.  TLCC and Red Sky users can load the \textbf{xyce} module to properly
set the environment. 

Several libraries (all freely available from Sandia National Laboratories or
other sites) are always required when building \Xyce{} from source.  These are:
\begin{XyceItemize}
\item Trilinos Solver Library version 11.6.1
  ({\color{XyceDeepRed}\url{http://trilinos.org}}).  Trilinos is a suite of
  packages that includes solver and partitioning libraries in parallel and
  serial, in addition to many other utilites.
\item UMFPACK version 4.1 and AMD version 1.0 (libumfpack.a, libamd.a)
  ({\color{XyceDeepRed}
  \url{http://www.cise.ufl.edu/research/sparse/umfpack/}}).  This is also
  provided by the SuiteSparse package that is available on many systems.
\item BLAS (Basic Linear Algebra Subprograms). This may be included with the
  compiler, or it may require separate package installation. One may also use
  ATLAS ({\color{XyceDeepRed} \url{http://math-atlas.sourceforge.net}}).
\item LAPACK (Linear Algebra PACKage). This may be included with the
  compiler, or it may require separate package installation. One may also use
  ATLAS ({\color{XyceDeepRed} \url{http://math-atlas.sourceforge.net}}).
\end{XyceItemize}
For parallel builds, the following libraries are additionally required:
\begin{XyceItemize}
\item Open MPI ({\color{XyceDeepRed}\url{http://www.open-mpi.org}}) library for
  message passing (version 1.4 or higher).  The version used to build Xyce must
  be the same that is used for building Trilinos.
\item ParMETIS ({\color{XyceDeepRed}
  \url{http://glaros.dtc.umn.edu/gkhome/metis/parmetis/overview}}) library for
  graph partitioning (version 3.1 or higher).  The MPI compiler used to compile
  ParMETIS must be the same that is used for Trilinos and Xyce.
\end{XyceItemize}

\section{\Xyce{} Release 6.1 Documentation}
The following \Xyce{} documentation is available at the \Xyce{} website in pdf
form.
\begin{XyceItemize}
\item \Xyce{} Release Notes, Version 6.1 (this document)
\item \Xyce{} Users' Guide, Version 6.1
\item \Xyce{} Reference Guide, Version 6.1
\item \Xyce{} Mathematical Formulation
\item Application Node: Using Open Source Schematic Capture Tools with \Xyce{}
\end{XyceItemize}
Also included at the \Xyce{} website as web pages are the following.
\begin{XyceItemize}
\item Building Guide (instructions for building Xyce from the source code)
\item Running the Xyce Regression Test Suite
\end{XyceItemize}

\section{New Features and Enhancements}

Highlights for \Xyce{} Release 6.1 include:
\begin{XyceItemize}
\item Simplified device code interface.
\item Improved robustness of Harmonic Balance analysis.
\item Improved voltage limiting handling for both the Trapezoid and Gear time integrators.
\item Parallel AC, harmonic balance and MPDE analysis.
\item Support for multi-input ($\geq$2) AND, NAND, OR and NOR gates and a new digital Buffer (BUF) model.
\item Improved compatibility between Xyce and PSpice digital device models.
\end{XyceItemize}
For details of each of these new features, see the \Xyce{} Users' Guide, the
\Xyce{} Installation Guide, and the \Xyce{} Reference Guide.  A more complete
listing of new features and improvements is given in the following sections.

\subsection{Device Support}

The device model package has been reworked to simplify the process of
adding new devices to \Xyce{}.

An alpha-release capability for using dynamic device plug-ins has
been added.  This feature is supported on Linux, Macintosh, FreeBSD,
and other true Unix-like operating systems.  Accessing this feature
requires that the user build \Xyce{} from source code; it is not
available in the pre-compiled binaries we provide.  In this initial
implementation, the feature is not yet supported in Cygwin builds on
Windows, nor is it supported on native Windows builds.

An example of using this capability is provided with the \Xyce{} source code in
the \texttt{user\_plugin} directory.  The example demonstrates how to use a
simple model defined in Verilog to create a new model in Xyce, and to use this
model directly as a plug-in without recompiling the rest of \Xyce{}.

Table~\ref{deviceListTable} contains a complete list of devices for \Xyce{}
Release 6.1.

% device list 
\input{deviceListTbl}

\subsection{Robustness Improvements}
\begin{XyceItemize}
\item Solver defaults have been modified for increased robustness of
  parallel runs with a minimum of user-specified options.
\end{XyceItemize}

% new device types:
\subsection{New Devices}
\begin{XyceItemize}
\item BSIM-CMG version 107.0.0.
%\item Uniform lumped LRC transmission line model.
\item Digital buffer model (BUF).
\item Multi-input ($\geq$2) AND, NAND, OR and NOR gates.
\end{XyceItemize}

\subsection{Enhanced Solver Stability, Performance and Features}
\begin{XyceItemize}
\item The AC, harmonic balance, and MPDE analysis features have been improved, and are now available in parallel builds of \Xyce{}.
\item Xyce has been updated to use Trilinos 11.6, which has resulted in significant performance improvements.
\end{XyceItemize}

%\subsection{Interface Improvements}
%\begin{XyceItemize}
%\item   
%\end{XyceItemize}

\newpage
\section{Defects of Release 6.0.1 Fixed in this Release}
\input{fixedDefectsTbl}

\newpage

\section{Known Defects and Workarounds}
\input{knownDefectsTbl}
\newpage

\section{Incompatibilities With Other Circuit Simulators}
\input{incompTbl}

\newpage
\section{Important Changes to \Xyce{} Usage Since the Release 6.0.1.}
Table ~\ref{newUsage} lists some usage changes for \Xyce{}.
\input{changesInputTbl}

\clearpage
% acknowledgements, trademarks, contact information.
\input{acktrade}
\begin{SANDdistribution}[NM]% or [CA]
    % \SANDdistCRADA	% If this report is about CRADA work
    % \SANDdistPatent	% If this report has a Patent Caution or Patent Interest
    % \SANDdistLDRD	% If this report is about LDRD work

    % External Address Format: {num copies}{Address}
%    \SANDdistExternal{}{}
    \bigskip

    % The following MUST BE between the external and internal distributions!
    % \SANDdistClassified % If this report is classified

    % Internal Address Format: {num copies}{Mail stop}{Name}{Org}
%    \SANDdistInternal{}{}{}{}

    % Mail Channel Address Format: {num copies}{Mail Channel}{Name}{Org}
%    \SANDdistInternalM{}{}{}{}
\end{SANDdistribution}


\end{document}
