% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2021 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).

% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2021 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


%%
%% Changes to Xyce input since the last release.
%%
{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\textbf{Change} &
  \color{white}\textbf{Detail} \\ \hline \endfirsthead
  \caption[]{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\textbf{Change} &
  \color{white}\textbf{Detail} \\ \hline \endhead

Continued support for FRAC\_MAX qualifier on TRIG-TARG measure lines &
For backwards compatibility with previous \Xyce{} versions for internal
users, \texttt{.OPTIONS MEASURE USE\_LTTM=<value>} has been added.  This
option defaults to 0, which uses the new version of the TRIG-TARG measure;
while setting it to 1 will use the old version of the TRIG-TARG measure
for all TRIG-TARG measures in the netlist.  If the FRAC\_MAX qualifier is
used on a TRIG-TARG line then \Xyce{} will automatically default to
\texttt{USE\_LTTM=1} for that particular measure line.  \\ \hline

\textbf{Gitlab-ex issue 338}: Added the function \texttt{Simulator:: getTimeVoltagePairsSz} & The function
\texttt{Simulator::getTimeVoltagePairsSz} supplies the maximun 
number of time, voltage or state values for an ADC in a subsequent call to 
\texttt{Simulator::getTimeVoltagePairs} or \texttt{Simulator::getTimeStatePairs}.
Also, calling \texttt{Simulator::getTimeStatePairs} no longer clears the voltage
history of an ADC, so a calling program that needs both state and voltage history
can first call \texttt{Simulator::getTimeStatePairs} and then call 
\texttt{Simulator::getTimeVoltagePairs} to get both.  Calling 
\texttt{Simulator::getTimeVoltagePairs} still clears the ADC history.
See the Application note, Mixed Signal Simulation with \Xyce{} 7.5 for further 
details. \\ \hline

\textbf{Gitlab-ex issue 348}:  Added the function \texttt{xyce\_getTimeVoltagePairs\-ADCLimitData()}  &
  A new function has been added to the \texttt{XyceCInterface} called 
  \texttt{xyce\_getTimeVoltagePairsADCLimitData()} which limits the data copied 
  to the caller allocated space to whatever maximum 
  allocation length is provided.  This avoids potential memory overwriting that
  could occur with the general access function \texttt{xyce\_getTimeVoltagePairsADC()}.
  See the Application note, Mixed Signal Simulation with \Xyce{} 7.5 for further details.  \\ \hline

\end{longtable}
}
