% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2019 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).



%%
%% Changes to Xyce input since the last release.
%%
{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endfirsthead
  \caption[]{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endhead

The behavior of \texttt{.PRINT HB\_FD} and \texttt{.PRINT HB\_TD} lines has changed & 
The \texttt{.PRINT HB\_FD} and \texttt{.PRINT HB\_TD} lines no longer produce
``fallback'' print lines.  They now only produce the \texttt{<netlistname>.HB.FD.prn} 
and \texttt{<netlistname>.HB.TD.prn} files, respectively. \\ \hline

The \texttt{FORMAT=PROBE} and \texttt{FORMAT=RAW} print formats for Harmonic
Balance (HB) output have changed & Those two print formats are still unsupported 
for HB output.  However, they now default to \texttt{FORMAT=STD} with file 
extensions that end in .prn. In earlier versions of \Xyce{}, some of those output 
files had extensions that ended with .unknown. In addition, all of those output 
files were in \texttt{FORMAT=NOINDEX} rather than \texttt{FORMAT=STD}.
\\ \hline

The use of the -r and -a command line options with a netlist that uses
\texttt{.HB} is now a parsing error &  Raw file output is not currently
supported for \texttt{.HB} analyses.  Previously, the \Xyce{} netlist 
would run but not produce any output files if the -r command line option 
was requested for a \texttt{.HB} analysis.  That case is now a netlist
parsing error.  \\ \hline

The filenames for the output files produced by \texttt{.PRINT AC} and
\texttt{.PRINT HB} lines that have \texttt{FILE=<name>} qualifiers
on them has changed & See the ``Multi-File Output for AC and HB Analyses'' 
subsection of the \Xyce{} Users' Guide for more information.  
\\ \hline

Error handling for the -remeasure command line option & In previous 
\Xyce{} releases, \texttt{-remeasure} would run even if all of the nodal
voltages, requested by the netlist's \texttt{.MEASURE} statements,
could not be parsed from the remeasured output file.  \Xyce{} will 
now generate an error for that case, since some of the re-measured 
values might be incorrect. \\ \hline

A .OP statement is required in the netlist to enable AC\_IC output & In
previous \Xyce{} releases, the \texttt{AC\_IC} output would be enabled,
for a netlist that used \texttt{.AC} analysis, if the netlist had
either a \texttt{.OP} statement or a \texttt{.STEP} statement.  A
\texttt{.OP} statement is now required to enable the \texttt{AC\_IC} 
output, which is consistent the documentation in the \Xyce{} Reference
Guide.

\\ \hline

\end{longtable}
}
