% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2019 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).



%%
%% Changes to Xyce input since the last release.
%%
{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endfirsthead
  \caption[]{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endhead

The \texttt{FORMAT=RAW} print format for homotopy output has changed &
The \texttt{FORMAT=RAW} print format is still unsupported for homotopy 
output.  However, it now defaults to \texttt{FORMAT=STD} with the file 
extension of .HOMOTOPY.prn. In earlier versions of \Xyce{}, the 
file extension was .HOMOTOPY.unknown. \\ \hline

The \texttt{FORMAT=PROBE} and \texttt{FORMAT=RAW} print formats for noise
output have changed & Those two print formats are still unsupported for 
noise output.  However, they now default to \texttt{FORMAT=STD} with the 
file  extensions of .NOISE.prn. In earlier versions of \Xyce{}, their 
file extensions were .NOISE\_unknown. \\ \hline

A \texttt{.PRINT HOMOTOPY} line is now required to get homotopy output
during a .transient simulation &  In previous versions of \Xyce{}, the 
contents of the \texttt{.PRINT TRAN} line was used to generate homotopy
output during a transient simulation if there was no \texttt{.PRINT 
HOMOTOPY} line in the netlist.  An explicit \texttt{.PRINT HOMOTOPY}
line is now required for all analyses types in order to generate 
\Xyce{} homotopy output.  \\ \hline

The simulation footers for \texttt{.PRINT HOMOTOPY} and \texttt{.PRINT SENS}
have changed slightly & For the \texttt{FORMAT=STD}, \texttt{FORMAT=GNUPLOT} 
and \texttt{FORMAT=TECPLOT} print formats, \texttt{.PRINT HOMOTOPY} will now print 
the simulation footer ``End of Xyce(TM) Homotopy Simulation'' for all simulations 
(with and without \texttt{.STEP}).  Similarly, \texttt{.PRINT SENS} will now
print the simulation footer ``End of Xyce(TM) Sensitivity Simulation'' for 
all simulations (with and without \texttt{.STEP}). \\ \hline

\end{longtable}
}
