% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2019 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).



%%
%% Changes to Xyce input since the last release.
%%
{
\small

\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{3.5in}}
  \caption{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endfirsthead
  \caption[]{Changes to netlist specification since the last release.\label{newUsage}} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Change &
  \color{white}\bf Detail \\ \hline \endhead


The default value for the NL parameter for the lossless transmission line
(T device) was changed & The default value for the NL (length in wavelengths) 
parameter for the lossless transmission line (T device) was changed from 
0 to 0.25 wavelengths. This default value matches SPICE3f5 and PSpice.
\\ \hline

\texttt{PRINT} qualifier added for \texttt{.MEASURE} lines.  & This qualifier
is available for all measure types  It allows the user to control where 
the measure output appears (suppressed, stdout only, \texttt{.mt0} file 
only or both places).  The default is both stdout and the \texttt{.mt0} file.
\\ \hline

\texttt{OUTPUT} qualifier added for \texttt{.MEASURE} lines  & This qualifier
is only available for the \texttt{MAX} and {MIN} measure types.  It allows the
user to control whether the measure's value or time (i.e., the maximum value
of the measured waveform or the time when that maximum value occurred) appears
in the \texttt{.mt0} file.  This qualifier does not affect the
descriptive output for the measure that is printed to standard output.

\end{longtable}
}
