% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2024 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


\index{\texttt{.OP}}
\index{analysis!op} \index{operating point analysis}
The .OP command causes detailed information about the bias point to be printed.

\begin{Command}\label{OP_COMMAND}

\format
.OP 

\comments

This type of analysis can be specified by itself, in which case \Xyce{}
will run a nominal operating point.  However, if specified with another
analysis type, no additional operating point will be calculated, as most
analyses require a DC operating point for initialization.

\texttt{.OP} outputs the parameters for all the device models
and all the device instances present in the circuit.  For large
circuits, this can be a very large amount of output, so use with
caution.

If no analysis command is provided, \texttt{.OP} will run a DC Operating
Point calculation (i.e., a DC analysis) with all the voltage sources 
left at their nominal (instance line) values.

The \Xyce{} \texttt{.OP} statement may provide less, or different, output than other simulators.  
For some of the missing quantities, a \Xyce{} \texttt{.PRINT} line can give similar information.  
Nodal voltages are always available  on a \texttt{.PRINT} line.  Device currents for many 
devices are available on a \texttt{.PRINT} line using the lead current notation 
\texttt{(I(devicename))}. Similarly, device power is available on a \texttt{.PRINT} line
via \texttt{P(devicename)} or \texttt{W(devicename)}.  However, these capabilities are not 
supported in all devices.  Table \ref{deviceFeatureSupportTable} shows which devices 
support these lead current and power notations.  Currently, there is no way to print 
out internal capacitances. 

\end{Command}

