% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2022 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


\label{Options_Reference}

\index{\texttt{.OPTIONS}} \index{analysis!options}  \index{analysis!control parameters} \index{solvers!control parameters}

Set various simulation limits, analysis control parameters
and output parameters.  In general, they use the following format:

\begin{Command}
\format
.OPTIONS <pkg> [<name>=<value>]*

\examples
.OPTIONS TIMEINT ABSTOL=1E-8

\arguments

\begin{Arguments}

\argument{pkg}

\begin{basedescript}{
    \desclabelstyle{\multilinelabel}
    \desclabelwidth{1.5in}
    \renewcommand{\makelabel}[1]{\tt #1\hfill}}
  \item[\tt DEVICE]       Device Model
  \item[\tt DIAGNOSTIC]   Diagnostic Simulation Output
  \item[\tt TIMEINT]      Time Integration
  \item[\tt NONLIN]       Nonlinear Solver
  \item[\tt NONLIN-TRAN]  Transient Nonlinear Solver
  \item[\tt NONLIN-HB]    HB Nonlinear Solver
  \item[\tt LOCA]         Continuation/Bifurcation Tracking
  \item[\tt LINSOL]       Linear Solver
  \item[\tt LINSOL-HB]    HB Linear Solver
  \item[\tt LINSOL-AC]    AC Linear Solver
  \item[\tt OUTPUT]       Output
  \item[\tt RESTART]      Restart
  \item[\tt SAMPLES]      Sampling analysis and non-intrusive Polynomial Chaos (PCE)
  \item[\tt EMBEDDEDSAMPLES]  EmbeddedSampling and non-intrusive Polynomial Chaos (PCE) 
  \item[\tt PCES]         Fully intrusive Polynomial Chaos (PCE)
  \item[\tt SENSITIVITY]  Direct and Adjoint sensitivities
  \item[\tt HBINT]        Harmonic Balance (HB)
  \item[\tt DIST]         Distribution
  \item[\tt MEASURE]      Measure
  \item[\tt PARSER]       Parsing
\end{basedescript}

\argument{\vbox{\hbox{name\hfil}\hbox{value}}}
The name of the parameter and the value it will be assigned.

\end{Arguments}

\comments

Exceptions to this format are the \texttt{OUTPUT} and \texttt{RESTART}
options, which use their own format. They are defined under their
respective descriptions.

The designator \texttt{pkg} refers loosely to a {\em module} in the
code.  Thus, the term is used here as identifying a specific module to
be controlled via {\em options} set in the netlist input file.

\end{Command}

\subsubsection{\texttt{.OPTIONS DEVICE} (Device Package Options)}
\index{device!package options}\index{\texttt{.OPTIONS}!\texttt{DEVICE}}

The device package parameters listed in Table~\ref{DevicePKG} outline the options
available for specifying device specific parameters.  Some of these (\texttt{DEFAS,
DEFAD, TNOM} etc.) have the same meaning as they do for
the \texttt{.OPTION} line from Berkeley SPICE (3f5).  Parameters which
apply globally to all device models will be specified here.
Parameters specific to a particular device instance or model are
specified in section~\ref{Analog_Devices}.

\input{devtbl}

\subsubsection{\texttt{.OPTIONS DIAGNOSTIC} (Diagnostic Simulation Output)}
\index{diagnostic!options}\index{\texttt{.OPTIONS}!\texttt{DIAGNOSTIC}}

This option enables the output of diagnostic data during a simulation to aid
in debugging circuit problems.  Currently the only diagnostic information 
available is the absolute value of the largest unknown in the solution vector.  
One can use the diagnostic option, \texttt{EXTREMALIMIT}, to set a limit above
which output will be sent to the diagnostic file set by \texttt{FILENAME}.  
Both the extrema and the circuit node associated with the extrema are 
written to the diagnostic file along with step information (time step in 
transient simulation and step number otherwise). A user can examine the 
extrema found in the solution vector to infer it the circuit simulation 
is performing as expected.

\input{diagnosticTbl.tex}


\subsubsection{\texttt{.OPTIONS TIMEINT} (Time Integration Options)}
\index{solvers!time integration!options}
\index{\texttt{.OPTIONS}!\texttt{TIMEINT}}

The time integration parameters listed in Table~\ref{TimeIntPKG} give the
available options for helping control the time integration algorithms for
transient analysis.

Time integration options are set using the \texttt{.OPTIONS TIMEINT} command.

\input{timetbl}


\subsubsection{\texttt{.OPTIONS NONLIN} (Nonlinear Solver Options)}
\index{solvers!nonlinear!options}\index{\texttt{.OPTIONS}!\texttt{NONLIN}}\index{\texttt{.OPTIONS}!\texttt{NONLIN-TRAN}}

The nonlinear solver parameters listed in Table~\ref{NonlinPKG} provide
methods for controlling the nonlinear solver for \index{DC analysis}
\index{analysis!DC} DC, \index{transient analysis}
\index{analysis!transient} transient and harmonic balance. Note that the
nonlinear solver options for DCOP, transient and harmonic balance are
specified in separate options statements, using \texttt{.OPTIONS
 NONLIN}, \texttt{.OPTIONS NONLIN-TRAN} and \texttt{.OPTIONS
 NONLIN-HB}, respectively. The defaults for  \texttt{.OPTIONS
 NONLIN} and \texttt{.OPTIONS NONLIN-TRAN} are specified in the
third and fourth columns of Table~\ref{NonlinPKG}.  The defaults for 
\texttt{.OPTIONS NONLIN-HB} are the same as the default settings given for
\texttt{NONLIN-TRAN} with two exceptions. For \texttt{NONLIN-HB}, the default
for \texttt{ABSTOL} is 1e-9 and the default for \texttt{RHSTOL} is 1e-4.

\input{nlstbl}

\index{solvers!nonlinear-transient!options}

\subsubsection{\texttt{.OPTIONS LOCA} (Continuation and Bifurcation Tracking Package Options)}
\index{solvers!continuation!options}
\index{solvers!homotopy!options}

The continuation selections listed in Table~\ref{ContinuationPKG}
provide methods for controlling continuation and bifurcation analysis.
These override the defaults and any that were set simply in the
continuation package.  This option block is only used if the nonlinear
solver or transient nonlinear solver enable continuation through the
\texttt{CONTINUATION} flag.

There are two specialized homotopy methods that can be set in the nonlinear
solver options line.  One is MOSFET-based homotopy, which is specific to MOSFET
circuits.  This is specified using \texttt{continuation=2} or
\texttt{continuation=mos}.  The other is GMIN stepping, which is specified
using \texttt{continuation=3} or \texttt{continuation=gmin}.  For either of
these methods, while it is possible to modify their default LOCA options, it is
generally not necessary to do so. Note that \Xyce{} automatically attempts GMIN
stepping if the inital attempt to find the DC operating point fails. If GMIN
stepping is specified in the netlist, \Xyce{} will not attempt to find a DC
operating point without GMIN stepping. 

LOCA options are set using the \texttt{.OPTIONS LOCA} command.\index{\texttt{.OPTIONS}!\texttt{LOCA}}

\input{locatbl}

\subsubsection{\texttt{.OPTIONS LINSOL} (Linear Solver Options)}
\index{solvers!linear!options}

\Xyce{} uses both sparse direct
solvers\index{solvers!linear!sparse-direct} as well as Krylov iterative
methods\index{solvers!linear!iterative (preconditioned Krylov methods)}
for the solution of the linear equations generated by Newton's method.
For the advanced users, there are a variety of options that can be set
to help improve these solvers.  Transformations of the linear system
have a ``\verb+TR_+'' prefix on the flag.  Many of the options for the
Krylov solvers are simply passed through to the underlying
Trilinos/AztecOO\index{Trilinos}\index{solvers!linear!Trilinos}\index{Aztec}\index{solvers!linear!Aztec}
solution settings and thus have an ``\verb+AZ_+'' prefix on the flag.

Linear solver options are set using the \texttt{.OPTIONS LINSOL}
command.\index{\texttt{.OPTIONS}!\texttt{LINSOL}}

\input{linsoltbl}

\subsubsection{\texttt{.OPTIONS LINSOL-HB} (Linear Solver Options)}

For harmonic balance (HB) analysis, \Xyce{} provides both iterative 
and direct methods for the solution of the steady state.  Only matrix-free techniques
are available for preconditioning the HB Jacobian with an iterative linear solver.
The direct linear solver explicitly forms the HB Jacobian and solves the complex-valued
linear system with the requested solver.
For HB analysis, a reduced number of linear solver options are available,  
and are set using the \texttt{.OPTIONS LINSOL-HB} command.\index{\texttt{.OPTIONS}!\texttt{LINSOL-HB}}

\input{hblinsoltbl}

\subsubsection{\texttt{.OPTIONS LINSOL-AC} (Linear Solver Options)}

For AC analysis, \Xyce{} provides both iterative and direct methods for the
solution of the linear equations. For the advanced users, there are a variety 
of options that can be set to help improve these solvers.  Transformations 
of the linear system have a ``\verb+TR_+'' prefix on the flag.  Many of the 
options for the Krylov solvers are simply passed through to the underlying
Trilinos/AztecOO\index{Trilinos}\index{solvers!linear!Trilinos}\index{Aztec}\index{solvers!linear!Aztec}
solution settings and thus have an ``\verb+AZ_+'' prefix on the flag.

Linear solver options are set using the \texttt{.OPTIONS LINSOL-AC}
command.\index{\texttt{.OPTIONS}!\texttt{LINSOL-AC}}  The available options
are the same as those for \texttt{.OPTIONS LINSOL}.


\subsubsection{\texttt{.OPTIONS OUTPUT} (Output Options)}

The \index{results!output options} \index{\texttt{.OPTIONS}!\texttt{OUTPUT}} \verb+.OPTIONS OUTPUT+
command can be used to allow control of the output frequency of data to files specified
by \index{\texttt{.TRAN}} \verb+.PRINT TRAN+ commands.  

One method is to specify output intervals.  The format for this method is:
\begin{vquote}
.OPTIONS OUTPUT INITIAL_INTERVAL=<interval> [<t0> <i0> [<t1> <i1>]* ]
\end{vquote}
where \verb+INITIAL_INTERVAL=<interval>+ specifies the starting interval time
for output and \verb+<tx> <ix>+ specifies later simulation times \verb+<tx>+
where the output interval will change to \verb+<ix>+. The solution is output at the
exact intervals requested; this is done by interpolating the solution
to the requested time points.

Another useful method for controlling the output frequency is to specify discrete output
points.  
\begin{vquote}
.OPTIONS OUTPUT OUTPUTTIMEPOINTS=<t0>,<t1>,* 
\end{vquote}
If this option is used, then only the specified time points will appear in the output file.
No other points will be output, so files using this method can be very sparse.  For this type
of output, the output values are not interpolated.  Instead, the specified output points are 
set as breakpoints in the time integrator, so the output values are computed directly.

In addition to controlling the frequency of output, it is also possible to use
output options to suppress the header from standard format output files, and the footer
from both standard and tecplot format output files.
\begin{vquote}
.OPTIONS OUTPUT PRINTHEADER=<boolean> PRINTFOOTER=<boolean>
\end{vquote}
where setting the \texttt{PRINTHEADER} variable to ``false'' will suppress the header and 
\texttt{PRINTFOOTER} variable to ``false'' will suppress the footer.  The \texttt{PRINTHEADER}
option is only applicable to \texttt{.PRINT <analysis> FORMAT=<STD|GNUPLOT|SPLOT>} files.
The \texttt{PRINTFOOTER} option is only applicable to
\texttt{.PRINT <analysis> FORMAT=<STD|GNUPLOT|SPLOT|TECPLOT>} files.

It is possible to add a \texttt{STEPNUM} column as the first column in the output file.
\begin{vquote}
.OPTIONS OUTPUT ADD\_STEPNUM\_COL=<boolean>
\end{vquote}
where setting the \texttt{ADD\_STEPNUM\_COL} variable to ``true'' will add the
\texttt{STEPNUM} column.  The default is ``false''. This option is applicable to
\texttt{FORMAT=<STD|NOINDEX|GNUPLOT|SPLOT>} for any \texttt{.PRINT} line that
supports \texttt{FORMAT=STD} output.

The default \Xyce{} output for phase operators, such as \texttt{VP()}, \texttt{IP()},
\texttt{SP()}, \texttt{YP()} and \texttt{ZP()}, is in degrees.  For compatibility with
other simulators like Spice3f5 and ngspice, it is possible to change that operator
output to use radians instead:
\begin{vquote}
.OPTIONS OUTPUT PHASE\_OUTPUT\_RADIANS=<boolean>
\end{vquote}
The default value for this option is FALSE.  If set to TRUE then the phase output
will be in radians instead of degrees.  This option also applies to the format
for AC sensitivity output.  It does not affect the output from a \texttt{.FOUR}
analysis or a texttt{.FOUR} measure though.  Those two outputs are always in degrees.

\subsubsection{\texttt{.OPTIONS RESTART} (Checkpointing Options)}

The \index{restart} \index{\texttt{.OPTIONS}!\texttt{RESTART}} \verb+.OPTIONS RESTART+ command is
used to control all \index{checkpoint} checkpoint output and restarting.

The checkpointing form of the \texttt{.OPTIONS RESTART} command takes the following format:
\Format{\par\tt .OPTIONS RESTART [PACK=<0|1>] JOB=<job prefix> \linebreak
+ [INITIAL\_INTERVAL=<initial interval time> [<t0> <i0> [<t1> <i1>]* ]]}

\texttt{PACK=<0|1>} indicates whether the restart data will be byte packed
or not.  Parallel restarts must always be packed while Windows/MingW
runs are always not packed.  Otherwise, data will be packed by default unless
explicitly specified.
\texttt{JOB=<job prefix>} identifies the prefix for restart files.  The
actual restart files will be the job name with the current simulation time
appended (e.g. \texttt{name1e-05} for \texttt{JOB=name} and simulation time
1e-05 seconds).  Furthermore, \texttt{INITIAL\_INTERVAL=<initial interval
  time>} identifies the initial interval time used for restart output.  The
\texttt{<tx> <ix>} intervals identify times \texttt{<tx>} at which the output
interval \texttt{(ix)} should change.  This functionality is identical to
that described for the \texttt{.OPTIONS OUTPUT} command.

\paragraph{Examples}

To generate checkpoints at every time step (default):

\Example{\texttt{.OPTIONS RESTART JOB=checkpt}}

To generate checkpoints every 0.1 $\mu s$:

\Example{\texttt{.OPTIONS RESTART JOB=checkpt INITIAL\_INTERVAL=0.1us}}

To generate unpacked checkpoints every 0.1 $\mu s$:

\Example{\texttt{.OPTIONS RESTART PACK=0 JOB=checkpt INITIAL\_INTERVAL=0.1us}}

To specify an initial interval of 0.1 $\mu s$, at 1 $\mu s$ change to interval
of 0.5 $\mu s$, and at 10 $\mu s$ change to interval of 0.1 $\mu s$:

\Example{\par\texttt{.OPTIONS RESTART JOB=checkpt INITIAL\_INTERVAL=0.1us 1.0us\linebreak + 0.5us 10us 0.1us}}

\subsubsection{\texttt{.OPTIONS RESTART} (Restarting Options)}

To restart from an existing restart file\index{restart!file}, specify the file
by either \texttt{FILE=<restart file name>} to explicitly use a restart file or
by \texttt{JOB=<job name> START\_TIME=<specified name>} to specify a file
prefix and a specified time.  The time must exactly match an output file time
for the simulator to correctly identify the correct file.  To continue
generating restart output files, \texttt{INITIAL\_INTERVAL=<interval>} and
following intervals can be appended to the command in the same format as
described above.  New restart files will be packed according to the previous
restart file read in.  

The restarting form of the \texttt{.OPTIONS RESTART} command takes the following format:

\Format{\par\tt .OPTIONS RESTART FILE=<restart file name>|JOB=<job name> START\_TIME=<time> \linebreak
    + [ INITIAL\_INTERVAL=<interval> [<t0> <i0> [<t1> <i1>]* ]]}

\paragraph{Examples}

Example restarting from checkpoint file at 0.133 $\mu s$:
\Example{\texttt{.OPTIONS RESTART JOB=checkpt START\_TIME=0.133us}}

To restart from checkpoint file at 0.133 $\mu s$:
\Example{\texttt{.OPTIONS RESTART FILE=checkpt0.000000133}}

Restarting from 0.133 $\mu s$ and continue checkpointing at 0.1 $\mu s$
intervals:
\Example{\par\texttt{
    .OPTIONS RESTART FILE=checkpt0.000000133 JOB=checkpt\_again\linebreak
    + INITIAL\_INTERVAL=0.1us
  }}

\subsubsection{\texttt{.OPTIONS RESTART}: special notes for use with two-level-Newton}
\index{restart!two-level}

Large parallel problems which involve power supply parasitics often
require a two-level solve, in which different parts of the problem
are handled separately.  In most respects, restarting a two-level
simulation is similar to restarting a conventional simulation.
However, there are a few differences:

\begin{XyceItemize}
\item When running with a two-level algorithm, \Xyce{} requires (at least) two
different input files.  In order to do a restart of a two-level \Xyce{}
simulation, it is necessary to have an \texttt{.OPTIONS RESTART} statement
in each file.

\item It is necessary for the statements to be consistent.  For example,
the output times must be exactly the same, meaning the initial intervals
must be exactly the same.

\item \Xyce{} will \emph{not} check to make sure that the restart
options used in different files match, so it is up to the user to ensure
matching options.

\item Finally, as each netlist that is part of a two-level solve will have its
own \texttt{.OPTIONS RESTART} statement, that means that each netlist
will generate and/or use its own set of restart files.  As a result,
the restart file name used by each netlist must be unique.
\end{XyceItemize}

\subsubsection{\texttt{.OPTIONS SAMPLES} (Sampling options)}
\index{solvers!sampling!options}

The sampling selections listed in Table~\ref{SamplesPKG}
provide methods for controlling Monte Carlo and Latin Hypercube Sampling methods.

SAMPLES options are set using the \texttt{.OPTIONS SAMPLES} command.\index{\texttt{.OPTIONS}!\texttt{SAMPLES}} 
They are only used if the netlist also includes a \texttt{.SAMPLING} statement. 

\input{samplestbl}

\subsubsection{\texttt{.OPTIONS EMBEDDEDSAMPLES} (Embedded Sampling options)}
\index{solvers!embeddedsampling!options}

The sampling selections listed in Table~\ref{EmbeddedSamplesPKG}
provide methods for controlling Embedded Sampling methods.

EMBEDDEDSAMPLES options are set using the \texttt{.OPTIONS EMBEDDEDSAMPLES}
command.\index{\texttt{.OPTIONS}!\texttt{EMBEDDEDSAMPLES}}  They are only used if the
netlist also includes a \texttt{.EMBEDDEDSAMPLING} statement.

\input{embeddedsamplestbl}

\subsubsection{\texttt{.OPTIONS PCES} (Fully intrusive PCE options)}
\index{solvers!pce!options}
\index{solvers!PCE!options}

The sampling selections listed in Table~\ref{PCEPKG}
provide methods for controlling Embedded Sampling methods.

PCES options are set using the \texttt{.OPTIONS PCES}
command.\index{\texttt{.OPTIONS}!\texttt{PCES}}  They are only used if the
netlist also includes a \texttt{.PCE} statement.

\input{pcestbl}

\subsubsection{\texttt{.OPTIONS SENSITIVITY} (Direct and Adjoint Sensitivity Options)}
\index{solvers!sensitivty!options}

The sensitivity selections listed in Table~\ref{SensitivityPKG}
provide methods for controlling direct and adjoint sensitivity analysis.

SENSITIVITY options are set using the \texttt{.OPTIONS SENSITIVITY} command.\index{\texttt{.OPTIONS}!\texttt{SENSITIVITY}} 
They are only used if the netlist also includes a \texttt{.SENS} statement. 

\input{sensitivitytbl}

\subsubsection{\texttt{.OPTIONS HBINT} (Harmonic Balance Options)}
\index{solvers!hb!options}\index{\texttt{.OPTIONS}!\texttt{HBINT}}

The Harmonic Balance parameters listed in Table~\ref{hbPKG} give the available
options for helping control the algorithm for harmonic balance analysis.

Harmonic Balance options are set using the \texttt{.OPTIONS HBINT} command.

\input{hboptiontbl}

\subsubsection{\texttt{.OPTIONS DIST} (Parallel Distribution Options)}
\index{dist!options}\index{\texttt{.OPTIONS}!\texttt{DIST}}

The parameters listed in Table~\ref{distPKG} give the available
options for controlling the parallel distribution used in \Xyce{}.
There are three choices for distribution strategy.

The default distribution strategy is ``first-come, first-served''
(\texttt{STRATEGY=0}), which divides the devices found in the netlist
into equal sized groups (in the order they are parsed) and distributes
a group to each processor.  This does not take into account the
connectivity of the circuit or balance device model computation, and
therefore can exhibit parallel imbalance for post-layout circuits that
have a substantial portion of parasitic devices.

The ``flat round-robin'' strategy (\texttt{STRATEGY=1}) will generate
the same distribution as the default strategy, but every parallel
processor will participate in reading its portion of the netlist.
This strategy provides a more scalable setup than the default
strategy, but can only be applied to flattened (non-hierarchical)
netlists.

The ``device balanced'' strategy (\texttt{STRATEGY=2}) will evenly
divide each of the device types over the number of parallel
processors, so each processor will have a balanced number of each
model type.  This allieviates the parallel imbalance in the device
model computation that can be experienced with post-layout circuits.
However, it does not take into account the circuit connectivity, so
the communication will not be minimized by this strategy.

\input{distoptiontbl}

\subsubsection{\texttt{.OPTIONS FFT} (FFT Options)}
\index{fft!options}\index{\texttt{.OPTIONS}!\texttt{FFT}}
The parameters listed in Table~\ref{fftPKG} give the available
options for controlling all of the \texttt{.FFT} statements in
a given \Xyce{} netlist.

If \texttt{FFT\_ACCURATE} is set to 1 (true), which is the default, then
\Xyce{} will insert breakpoints at the sample times requested by the
collection of \texttt{.FFT} lines in the netlist.  This has been found
to improve the accuracy of the \texttt{.FFT} analyses, at the possible
expense of simulation speed.  If \texttt{FFT\_ACCURATE} is set to
0 (false), then interpolation is used to determine the output variable
values at the specified sample times.  If the \texttt{-remeasure} command
line option is used to recalculate the \texttt{.MEASURE FFT} and/or
\texttt{.FFT} statements for a \texttt{.TRAN} analysis, then
\texttt{FFT\_ACCURATE} is set to 0 during the re-measure operation.  Finally,
if \texttt{.OPTIONS OUTPUT INITIAL\_INTERVAL} is used in the netlist
then \texttt{.OPTIONS FFT FFT\_ACCURATE} will also be set to 0.

If \texttt{FFTOUT} is set to 1 then additional metrics are output to both stdout
and the \verb+<netlistName>.fft0+ file for each \texttt{.FFT} line.  In
addition a sorted list of the 30 largest harmonics is output to stdout.
Those additional metrics are as follows, where Section \ref{FFT_metrics}
provides detailed definitions for these metrics:

\begin{itemize}
  \item Effective Number of Bits (ENOB)
  \item Spurious Free Dynamic Range (SFDR)
  \item Signal to Noise Ratio (SNR)
  \item Signal to Noise-and-Distortion Ratio (SNDR)
  \item Total Harmonic Distorion (THD)
\end{itemize}

The setting for \texttt{FFT\_MODE} is used to control whether the \Xyce{} FFT
processing and output are more compatible with HSPICE (0) or Spectre (1).
This setting affects the format of the window functions, the conversion from
two-sided to one-sided results, and whether the default output for the
magnitude values is normalized, or not.  Section~\ref{FFT_MODE} gives
more details.

\input{fftoptiontbl}

\subsubsection{\texttt{.OPTIONS MEASURE} (Measure Options)}
\index{measure!options}\index{\texttt{.OPTIONS}!\texttt{MEASURE}}
The parameters listed in Table~\ref{measurePKG} give the available
options for controlling all of the \texttt{.MEASURE} statements in
a given \Xyce{} netlist.  The \texttt{MEASDGT}, \texttt{MEASFAIL}
and \texttt{MEASOUT} options are included for HSPICE compatibility.

If given in the netlist, the setting for \texttt{MEASOUT} controls whether 
the \texttt{.mt\#} (or \texttt{.ms\#} or \texttt{.ma\#}) files are made (1) or not (0). 
The \texttt{MEASOUT} setting takes precedence over the \texttt{MEASPRINT} setting 
(which is a Xyce-specific option) if both are given in the netlist.
See Section \ref{Measure_Suppressing_Measure_Output} for more details then on 
how the \texttt{MEASPRINT} option interacts with the individual 
\texttt {.MEASURE} statements and the \texttt{-remeasure} command 
line option.

If given in the netlist, the setting for the \texttt{MEASDGT} overrides the 
\texttt{PRECISION} qualifiers given on individual \texttt{.MEASURE} lines. 
The default value for the \texttt{MEASDGT} option is different from in HSPICE.

The \Xyce{} behavior for failed measures can be controlled via the \texttt{MEASFAIL}
and \texttt{DEFAULT\_VAL} options, as well as with the \texttt{DEFAULT\_VAL} 
qualifiers on individual \texttt{.MEASURE} lines.  The order of precedence is
the \texttt{DEFAULT\_VAL} option and then the \texttt{DEFAULT\_VAL} qualifier on
individual \texttt{.MEASURE} lines.  If \texttt{MEASFAIL=0} then \Xyce{} outputs
the default value in the \texttt{.mt\#} ( or \texttt{.ms\#} or \texttt{.ma\#})
files for a failed measure.  If \texttt{MEASFAIL=1} (or any other non-zero 
value) then \Xyce{} outputs ``FAILED'' in the \texttt{.mt\#} ( or \texttt{.ms\#} or \texttt{.ma\#}) 
files for a failed measure.  If given in the netlist, the setting for the 
\texttt{DEFAULT\_VAL} option overrides the \texttt{DEFAULT\_VAL} qualifiers given 
on individual \texttt{.MEASURE} lines.  The \texttt{DEFAULT\_VAL} option and the 
\texttt{DEFAULT\_VAL} qualifiers can be set to any real number.  For all of these 
cases, \Xyce{} will print ``FAILED'' to the standard output for a failed measure.
As a final note, the \texttt{FOUR} measure is a special case since it produces multiline
output.  Failed \texttt{FOUR} measures will be reported as ``FAILED'' in the
\texttt{.mt\#} ( or \texttt{.ms\#} or \texttt{.ma\#}) files, irrespective of the various
\texttt{MEASFAIL} and \texttt{DEFAULT\_VAL} settings.

The \texttt{USE\_CONT\_FILES} option controls whether each \texttt{AC\_CONT},
\texttt{DC\_CONT}, \texttt{NOISE\_CONT} or \texttt{TRAN\_CONT} mode measure uses
a separate output file for its results, or not. Section~\ref{Measure_CONT_Measurement_Output}
provides more details and an example netlist for this options setting.

For backwards compatibility with previous \Xyce{} versions, \texttt{USE\_LTTM} has
been added.  This option defaults to 0, which uses the new version of the \texttt{TRIG-TARG}
measure; while setting it to 1 will use the old version of the \texttt{TRIG-TARG} measure
for all \texttt{TRIG-TARG} measures in the netlist.  If the \texttt{FRAC\_MAX} qualifier
is used on a \texttt{TRIG-TARG} line then \Xyce{} will automatically default to
\texttt{USE\_LTTM=1} for that particular measure line.  It is anticipated that this
option setting will be removed at some point.

\input{measureoptiontbl}

\subsubsection{\texttt{.OPTIONS PARSER} (Parser Options)}
\index{parser!options}\index{\texttt{.OPTIONS}!\texttt{PARSER}}
The parameter listed in Table~\ref{parserPKG} gives the available
option for netlist parsing.

\input{parseroptiontbl}


