% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2020 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


\index{\texttt{.SAMPLING}}
\index{analysis!sampling} \index{sampling analysis}
Calculates a full analysis (\verb|.DC|, \verb|.TRAN|, \verb|.AC|, etc.) over a distribution of
parameter values.  Sampling operates similarly to \verb|.STEP|, except that the parameter
values are generated from random distributions rather than sweeps.  

\index{analysis!SAMPLING} 
\index{SAMPLING analysis}
\index{analysis!MC} 
\index{MC analysis}
\index{analysis!Monte Carlo} 
\index{Monte Carlo analysis}
\index{analysis!LHS} 
\index{LHS analysis}
\index{Latin Hypercube Sampling analysis}

\begin{Command}
\format
.SAMPLING  \\
+ param=<parameter name>,[parameter name]*  \\
+ type=<parameter type>,[parameter type]*  \\
+ means=<mean>,[mean]*  \\
+ std\_deviations=<standard deviation>,[standard deviation]* 

\examples
\begin{alltt}
.SAMPLING
+ param=R1
+ type=normal
+ means=3K
+ std\_deviations=1K

.SAMPLING
+ param=R1,R2
+ type=uniform,uniform
+ lower\_bounds=1K,2K
+ upper\_bounds=5K,6K

.options SAMPLES numsamples=10000

.options SAMPLES numsamples=25000
+ OUTPUTS=\{R1:R\},\{V(1)\}
+ SAMPLE\_TYPE=MC

.options SAMPLES numsamples=1000
+ MEASURES=maxSine
+ SAMPLE\_TYPE=LHS

.options samples numsamples=30
+ covmatrix=1e6,1.0e-3,1.0e-3,4e-14
+ OUTPUTS=\{V(1)\},\{R1:R\},\{C1:C\}
\end{alltt}

\arguments

\begin{Arguments}

\argument{param}
Names of the parameters to be sampled.  This may be any of the parameters that are valid 
for \verb|.STEP|, including device instance, device model, or global parameters.  
  If more than one parameter, then specify as a comma-separated list.

\argument{type}
Distribution type for each parameter.  This may be uniform or normal.  
  If more than one parameter, then specify as a comma-separated list.

\argument{means}
If using normal distributions, the mean for each parameter must be specified.
  If more than one parameter, then specify as a comma-separated list.

\argument{std\_deviations}
If using normal distributions, the standard deviation for each parameter must be specified.
  If more than one parameter, then specify as a comma-separated list.

\argument{lower\_bounds}
If using uniform distributions, the lower bound must be specified.  This is optional for normal distributions.  
  If used with normal distributions, may alter the mean and standard deviation.
  If more than one parameter, then specify as a comma-separated list.

\argument{upper\_bounds}
If using uniform distributions, the upper bound must be specified.  This is optional for normal distributions.
  If used with normal distributions, may alter the mean and standard deviation.
  If more than one parameter, then specify as a comma-separated list.

\end{Arguments}

\comments

In addition to the \verb|.SAMPLING| command, this analysis requires a 
  \verb|.options SAMPLES| command as well.  The \verb|.SAMPLING| command specifies 
  parameters and their attributes.  The \verb|.options SAMPLES| command specifies 
  analysis options, including the number of samples, the type of sampling (LHS or MC), 
  and the outputs and/or measures for which to compute statistics.

On the \verb|.SAMPLING| command line, parameters and their attributes must be specified 
  using comma-separated lists.  The comma-separated lists must all be the same length.

\end{Command}

