% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2024 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


%%
%% Sampling Options Table
%%
\index{solvers!sampling!options}
\begin{OptionTable}{Options for Sampling Package.} \label{SamplesPKG}
NUMSAMPLES   & Total number of samples & 0 \\ \hline
SAMPLE\_TYPE & Sampling type (MC or LHS) & MC \\ \hline
OUTPUTS      & Comma separated list of outputs (anything that would be a valid \texttt{.RESULT} output command) & -- \\ \hline
MEASURES     & Comma separated list of measure names (must refer to \texttt{.MEASURE} commands in the netlist) & -- \\ \hline
COVMATRIX    & Covariance matrix specified in row major form as comma-separated double precision numbers. & -- \\ \hline
SEED         & Random seed & See footnote.\footnotemark[1] \\ \hline
OUTPUT\_SAMPLE\_STATS   &  Compute and outputs statistics for specified outputs and/or measures. & -- \\ \hline
REGRESSION\_PCE    & Enable regression based PCE.  If this is enabled, the randomly sampled points will be used to produce a PCE approximation using regression methodss.     & -- \\ \hline
PROJECTION\_PCE    & Enable projection based PCE (quadrature).  If this is enabled, a PCE approximation will be created using quadrature methods.  The NUMSAMPLES parameter will be ignored, and the samples will be the quadrature points used by projection PCE.     & -- \\ \hline
RESAMPLE    & Once the PCE coefficients are obtained, perform sampling on the PCE approximation & -- \\ \hline
OUTPUT\_PCE\_COEFFS    & Output the PCE coefficients & -- \\ \hline
SPARSE\_GRID    &  Use sparse grid methods if using projection PCE.    & -- \\ \hline
STDOUTPUT    &  Send sampling and PCE output to the terminal   & -- \\ \hline
\end{OptionTable}

\footnotetext[1]{The seed can also be set using command line option, -randseed.   The command line seed will override the netlist seed value.  If the seed is not set in either the netlist or on the command line, then Xyce generates a seed internally.  In all cases, \Xyce{} will output text to the console indicating what seed is being used.}  

