% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2021 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


%%
%%  Table of Windows Issues.
%%

\index{Microsoft Windows}
\label{Windows_Issues}
\begin{longtable}[h] {>{\raggedright\small}m{2in}|>{\raggedright\let\\\tabularnewline\small}m{4in}}
  \caption{Issues for Microsoft Windows.} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Issue &
  \color{white}\bf Comment \\ \hline \endfirsthead
  \caption[]{Issues for Microsoft Windows.} \\ \hline
  \rowcolor{XyceDarkBlue}
  \color{white}\bf Issue &
  \color{white}\bf Comment \\ \hline \endhead

File names are case-sensitive &
\Xyce{} will expect library files, which are referenced in the netlist, to have
exactly the same case as the actual filename.  If not, \Xyce{} will be unable
to find the library file.  \\ \hline

Windows endline characters are different from other OS's &
The characters that mark the end of a line in Windows are a carriage return
followed by a Line Feed (\texttt{CR+LF}).  In Unix-like systems (including
Linux and OS X), the character is simply a Line Feed (\texttt{LF}).  Moving a
file between the two systems does not usually cause issues, but users should be
aware of the difference in case problems arise.  \\ \hline

\Xyce{} is unable to read proprietary file formats. &
Programs such as Microsoft Word by default use file formats that \Xyce{} cannot
recognize.  It is best not to use such programs to create netlists, unless
netlists are saved as *.txt files.   If you must use a Microsoft editor, it is
better to use Microsoft Notepad.  In general, the best solution is to use a
Unix-style editor, such as Vi, Gvim, or Emacs.  \\ \hline

\end{longtable}


%%% Local Variables:
%%% mode: latex
%%% End:
