% Sandia National Laboratories is a multimission laboratory managed and
% operated by National Technology & Engineering Solutions of Sandia, LLC, a
% wholly owned subsidiary of Honeywell International Inc., for the U.S.
% Department of Energy’s National Nuclear Security Administration under
% contract DE-NA0003525.

% Copyright 2002-2021 National Technology & Engineering Solutions of Sandia,
% LLC (NTESS).


\chapter{Netlist Reference}
\label{Netlist_Reference}
\index{netlist!reference}

\chapteroverview{Chapter Overview}
{
This chapter contains reference material directed towards working with circuit
analyses in \Xyce{} using the netlist interface.  Included are
detailed command descriptions, start-up option definitions and a list of
devices supported by the \Xyce{} netlist interface.
}

\section{Netlist Commands}
\label{Netlist_Commands}
\index{netlist!commands}

This section outlines the netlist commands that can be used with \Xyce{} to
setup and control circuit analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\newpage
\subsection{\texttt{.AC} (AC Analysis) }
\index{\texttt{.AC}}
\index{analysis!AC} \index{AC analysis}
\input{AC_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.DATA} (Data Table for sweeps) }
\index{\texttt{DATA}}
\input{DATA_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.DC} (DC Sweep Analysis) }
\index{\texttt{DC}}
\index{analysis!DC} \index{DC analysis}
\input{DC_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.DCVOLT} (Initial Condition, Bias point)}
\index{\texttt{.DCVOLT}}
\index{initial condition!DCVOLT}
\index{initial condition}

The \texttt{.DCVOLT} sets initial conditions for an operating point calculation.
It is identical in function to the \texttt{.IC} command.  See
section~\ref{IC_section} for detailed guidance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.EMBEDDEDSAMPLING} (Embedded Sampling)}\label{.EMBEDDEDSAMPLING}
\input{EMBEDDEDSAMPLING_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.END} (End of Circuit)}
Marks the end of netlist file.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.ENDS} (End of Subcircuit)}
Marks the end of a subcircuit definition.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.FFT} (FFT Analysis)}
\index{\texttt{.FFT}}
\input{FFT_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.FOUR} (Fourier Analysis)}
\index{\texttt{.FOUR}}
\input{FOUR_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.FUNC} (Function)}
\index{\texttt{.FUNC}}
\input{FUNC_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.GLOBAL} (Global Node)}
\index{\texttt{.GLOBAL}}
\input{GLOBAL_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.GLOBAL\_PARAM} (Global parameter)}
\index{\texttt{.GLOBAL\_PARAM}}
\input{GLOBAL_PARAM_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.HB} (Harmonic Balance Analysis)}
\input{HB_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.IC} (Initial Condition, Bias point)}
\index{\texttt{.IC}}
\input{IC_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.INC or .INCLUDE or .INCL} (Include file)}
\index{\texttt{.INC}}
\input{INCLUDE_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.LIB} (Library file)}
\index{\texttt{.LIB}}
\input{LIB_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.LIN} (Linear Analysis)}
\index{\texttt{.LIN}}
\input{LIN_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.MEASURE or .MEAS} (Measure output)}
\index{output!control}
\index{results!output control}
\index{\texttt{.MEASURE}}
\input{MEASURE_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.MEASURE FFT} (Measure output for .FFT)}
\index{output!control}
\index{results!output control}
\index{\texttt{.MEASURE FFT}}
\input{MEASURE_FFT_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.MODEL} (Model Definition)}
\index{model!definition}
\input{MODEL_Command}

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \newpage
%% \subsection{\texttt{.MPDE} (Multi-Time Partial Differential Equation Analysis)}
%% \input{MPDE_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.NODESET} (Approximate Initial Condition, Bias point)}
\input{NODESET_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.NOISE} (Noise Analysis) }
\index{\texttt{.NOISE}}
\index{analysis!Noise} \index{Noise analysis}
\input{NOISE_Command}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.OP} (Bias Point Analysis)}
\input{OP_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.OPTIONS} Statements}
\input{OPTIONS_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.PARAM} (Parameter)}
\index{\texttt{.PARAM}}
\input{PARAM_Command}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{PREPROCESS_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.PRINT} (Print output)}\label{.PRINT}
\input{PRINT_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.RESULT} (Print results)}\label{.RESULT}
\input{RESULT_Command}

%%{%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.SAMPLING} (Sampling UQ Analysis)}\label{.SAMPLING}
\input{SAMPLING_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.SAVE} (Save operating point conditions)}
\input{SAVE_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.SENS} (Compute DC, AC or transient sensitivities)}
\label{SensitivityAnalysis}
\input{SENS_Command}

%%{%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.STEP} (Step Parametric Analysis)}\label{.STEP}
\input{STEP_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.SUBCKT} (Subcircuit)}
\label{SubcircuitDefinition}
\index{subcircuit}
\input{SUBCKT_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{\texttt{.TRAN} (Transient Analysis)}
\input{TRAN_Command}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{Miscellaneous Commands}
\subsubsection{\texttt{*} (Comment)}
\index{netlist!comment} A netlist comment line.  Whitespace at
the beginning of a line is also interpreted as a comment unless it
is followed by a \verb|+| symbol, in which case it treats the line as a continuation.

\subsubsection{\texttt{;} (In-line Comment)}
\index{netlist!in-line comment} Add a netlist in-line comment.

\subsubsection{\texttt{+} (Line Continuation)}
\index{netlist!line continuation} Continue the text of the previous line.

\newpage
\section{Expressions}
\label{ExpressionDocumentation}
\Xyce{} supports use of mathematical expressions in several contexts:
\begin{XyceItemize}
\item for the values of device instance and model parameters.
\item in definition of parameters in \texttt{.PARAM} and \texttt{.GLOBAL\_PARAM} statements.
\item for output on \texttt{.PRINT} lines.
\end{XyceItemize}

In all contexts where expressions are allowed, they should be enclosed
in braces (\{\}).  For netlist compatibility with other simulators
they may be enclosed in single quotation marks instead (\texttt{'}),
but these are simply replaced with braces at a very early stage of
netlist parsing.  It is recommended that the braces be used in
netlists written specifically for \Xyce{}.

The expression package in \Xyce{} supports all standard arithmetic
operators, trigonometric functions, a collection of arithmetic
functions, and some functions to mimic the pulse, sine, exp, and sffm
time-dependent functions in the independent current and voltage sources.
These functions are listed in tables \ref{Arithmetic_Functions} and
\ref{SPICE_Functions}.

\paragraph{Operators}
\index{netlist!expression operators}
\index{expressions!operators}
\input{Expression_Operator}

\paragraph{Special note on ternary operator}
Note that the ternary operator is available for use in \Xyce{}.  This
operator is the same as the ternary conditional operator in C, C++,
Perl, and others.  The ternary expression \texttt{t?a : b} is
equivalent to the function \texttt{IF(t,a,b)} described below.
However, please be aware that the ternary operator has extremely low
precedence just as it has in these other languages, and if parentheses
are not used to make explicit which expressions are supposed to be
part of the condition or true and false values, the resolution of the
expression may be surprising.

For example, the expression
\begin{alltt}
  1+a==b?1:0+1
\end{alltt}
is equivalent to the expression
\begin{alltt}
  IF(1+a==b,1,0+1)
\end{alltt}
because the ``+'' and ``=='' operators have higher precedence than
either ``?'' or ``:''.  Similarly:
\begin{alltt}
  A==B?1:0 + A==C?2:0 + A==D?3:0
\end{alltt}
is equivalent to
\begin{alltt}
  if(A==B,1,IF(0 + A==C,2,IF(0 + A==D,3,0)))
\end{alltt}
Given the way the original expression is written, it appears that the
intent was that the expression be evaluated as:
\begin{alltt}
  If(A==B,1,0) + IF(A==C,2,0) + IF(A==D,3,0)
\end{alltt}
This is not how the expression will be evaluated.  Fortunately,
because of the use of ``0'' to the right of the colons in each case,
the expression just happens to give the desired result in either
interpretation, but Xyce is using the nested IF equivalent.

Finally, due to restrictions on the expression parser, {\bf it is essential
that ternary operators never be written so that a bare parameter is
directly to the left of a colon}.  This is because colons are actually
legal characters in parameters --- the colon represents hierarchy, so
that \texttt{R1:R} means the R parameter of device R1, and
\texttt{X1:A} refers to the node A of subcircuit X1.  Therefore, it is
necessary to put at least one character that is invalid in parameter names
in between the colon and the parameter.  It is sufficient to use a space.
\begin{alltt}
    {\color{red} (A==B)?C:D}  ; this expression will generate a syntax error
    {(A==B)?C :D}  ; this expression is acceptable
    {(A==B)?C+0:D}  ; this expression is acceptable
    {(A==B)?(C):D}  ; this expression is acceptable
\end{alltt}

\paragraph{Arithmetic Functions}
\input{Expression_Arithmetic_Functions}

\paragraph{Spice Compatable Functions}
\index{netlist!functions}
\index{expressions!SPICE functions}
\input{Expression_Spice_Functions}

Information about the restrictions on expressions in specific contexts
is given in the subsections that follow.

\subsection{Expressions in \texttt{.PARAM} or \texttt{.GLOBAL\_PARAM} Statements}

Expressions used in \texttt{.PARAM} statements are the most highly
constrained.  They must evaluate to a constant at the beginning of a
run, and therefore must involve only numerical constants and other
previously defined \texttt{.PARAM}s.  The value of the parameter will
be computed when the netlist is parsed, and will replace the name
wherever it is used.

\Example{.PARAM SQUARES=5.0}
\Example{.PARAM SHEETRES=25}
\Example{.PARAM RESISTANCE=\{SQUARES*SHEETRES\}}

Global parameters are somewhat less constrained.  These parameters are
allowed to depend on parameters defined in \texttt{.PARAMS} or
\texttt{.GLOBAL\_PARAMS} statements, and may contain special variables
such as \textrm{TIME}, \textrm{FREQ}, \textrm{TEMP} or \textrm{VT}.  They
may not contain any references to solution variables or lead currents.

\Example{.PARAM dTdt=.01}
\Example{.GLOBAL\_PARAM Temperature=\{27+dTdt*TIME\}}

\subsection{Expressions in \texttt{.PRINT} Lines}

Expressions on \texttt{.PRINT} lines may contain references to
parameters defined in either \texttt{.PARAM} or
\texttt{.GLOBAL\_PARAM} statements, device parameters using the syntax
\texttt{<device name>:<parameter name>}, and may also contain solution
variables.

\begin{centering}
\shadowbox{
\begin{minipage}{0.8\textwidth}
\begin{vquote}
\color{blue}*example with .print expressions\color{black}
.PARAM RES=50
R1 1 0 \{RES\}
V1 1 0 sin(0 5 100khz)
.tran 1u 1m
*Print power dissipated through resistor,
*and actual resistance used in the R1
*device
.print tran \{V(1)*V(1)/RES\} \{R1:R\}
.end
\end{vquote}
\end{minipage}
}
\end{centering}

\subsection{Limitations on Using Complex Values in Expressions}
\label{ComplexExpressions}
The \Xyce{} expression library was written to work with complex
quantities, and can perform complex arithmetic on any set of 
complex inputs to produce a complex output.
However, the default behavior is to print only the real part 
for expressions on the print line.  If the user desires both the
real and imaginary part, it is necessary to use operators 
such as \texttt{Re()} and \texttt{Img()} as follows:

\begin{vquote}
.PRINT AC  \{RE(V(N0,N1))\} \{IMG(V(N0,N1))\}
\end{vquote}

Note that this is only necessary to obtain the specific components 
final result.   It isn't necessary to manually specify real equivalent 
arithmetic expressions to do complex math, although that will work.  Complex 
arithmetic will happen automatically within the expression.  So, for example,
the following will work to produce the magnitude of the product of two 
complex-valued voltage nodes:

\begin{vquote}
.PRINT AC  \{M(V(N1)*V(N0))\}
\end{vquote}

\subsection{Expressions for Device Instance and Model Parameters}

Expressions of constants and \texttt{.PARAM} parameters may be used
for the values of any device parameters in instance and model lines.

Except in very specific devices, expressions used for device parameter
values must evaluate to a time-independent constant, and must not
contain dependence on solution variables such as nodal voltages or
currents.  In these cases, \texttt{.GLOBAL\_PARAM} parameters may also
be used as long as they are not time-dependent.

\begin{centering}
\shadowbox{
\begin{minipage}{0.8\textwidth}
\begin{vquote}
\color{blue}*example of use of expressions for device parameters \color{black}
.PARAM RES=50
.GLOBAL\_PARAM theSaturationCurrent=1.5e-14
R1 1 0 \{RES\}
V1 1 0 sin(0 5 100khz)
D1 1 0 DMODEL
.MODEL D DMODEL IS={theSaturationCurrent}

.step theSaturationCurrent 1e-14 5e-14 1e-14
\end{vquote}
\end{minipage}
}
\end{centering}

Some parameters of specific devices are exceptions to the general
rule.  These parameters have no restrictions and may depend on any
parameters, time, or solution variables in the
netlist:
\begin{XyceItemize}
\item The \textrm{V} or \textrm{I} instance parameters of the
  \texttt{B} source.
\item The \textrm{CONTROL} instance parameter of the switch (\texttt{S}
  device).
\item The \textrm{C} (capacitance) instance parameter for the capacitor.
\item The coupling coefficient instance parameter for the {\em LINEAR}
  mutual inductor (\texttt{K} device with no model card specified)
\end{XyceItemize}

These specific instance parameters may be time-depdendent (i.e. they
may reference the \texttt{TIME} special variable), but may not depend
on any solution variables:

\begin{XyceItemize}
\item The \textrm{TEMP} instance parameter of all devices.
\item The \textrm{L} (inductance) parameter of the inductor.
\item The \textrm{R} (resistance) parameter of the resistor.
\item The \textrm{R}, \textrm{RESISTIVITY}, \textrm{DENSITY}, \textrm{HEATCAPACITY} and \textrm{THERMAL\_HEATCAPACITY} parameters of the thermal resistor (resistor level 2).
\end{XyceItemize}
%\newpage

%%
%% PSpice POLY
%\clearpage
\subsection{POLY expressions}
\label{PspicePoly}
\index{analog behavioral modeling!POLY}
\index{analog behavioral modeling!polynomial expression}
\index{POLY}
\input{POLY_Keyword}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Devices}
\label{Analog_Devices}
\index{device!analog}

\Xyce{} supports many devices, with an emphasis on analog devices, including
sources, subcircuits and behavioral models.  This section serves as a reference
for the devices supported by \Xyce{}.  Each device is described separately and
includes the following information, if applicable:
\begin{XyceItemize}
\item a description and an example of the correct netlist syntax.
\item the matching model types and their description.
\item the matching list of model parameters and associated descriptions.
\item the corresponding
%circuit diagram and
 characteristic equations for the model (as required).
\item references to publications on which the model is based.
\end{XyceItemize}
User-defined models may be implemented using the \index{netlist!model
definition}\index{\texttt{.MODEL}} \texttt{.MODEL} (model definition)
statement, and macromodels can be created as subcircuits using the
\index{netlist!subcircuit} \texttt{.SUBCKT}\index{\texttt{.SUBCKT}}
(subcircuit) statement.

Please note that the characteristic equations\index{device!equations} are
provided to give a general representation of the device behavior.  The actual
\Xyce{} implementation of the device may be slightly different in order to
improve, for example, the robustness of the device.

Table~\ref{Device_Summary} gives a summary of the device types and the form of
their netlist formats.  Each of these is described below in detail.

\input{analogtbl}

\input{deviceFeatureSupportTbl}

\clearpage
\subsection{Voltage Nodes}
\label{Voltage_Nodes}
\index{device!nodes} \index{Voltage Nodes} \index{netlist!nodes}

Devices in a netlist are connected between {\em nodes}, and all device
types in \Xyce{} require at least two nodes on each instance line. Section
~\ref{legalCharacters} lists the characters that are legal and illegal in
\Xyce{} node and device names.

Except for global nodes (below), voltage node names appearing in a
subcircuit that are not listed in the subcircuit's argument list are
accessible only to that subcircuit; devices outside the subcircuit
cannot connect to local nodes.

\subsubsection{Global nodes}
A special syntax is used to designate certain nodes as {\em global}
nodes.  Any node whose name starts with the two characters ``\$G'' is
a global node, and such nodes are available to be used in any
subcircuit.  A typical usage of such global nodes is to define a \texttt{VDD}
or \texttt{VSS} signal that all subcircuits need to be able to access, but
without having to provide \texttt{VSS} and \texttt{VDD} input
nodes to every subcircuit.  In this case, a global \texttt{\$GVDD} node
would be use for the VDD signal.

The node named \texttt{0} is a special global node.  Node \texttt{0}
is always ground, and is accessible to all levels of a hierarchical
netlist.

For compatibility with HSPICE, the \texttt{.GLOBAL} command can
be used to define global nodes that do not start with the two
characters ``\$G''.  See section \ref{GLOBAL_section} for more details.

\subsubsection{Subcircuit Nodes}

Hierarchical netlists may be created using
\texttt{.SUBCKT} [\ref{SubcircuitDefinition}] to define common subcircuit
types, and \texttt{X} [\ref{SubcircuitInstance}] lines to create
instances of those subcircuits.  There are two types of nodes
associated with such subcircuits, {\em interface\/} nodes and {\em
internal\/} nodes.

Interface nodes are the nodes named on the \texttt{.SUBCKT} line.
These are effectively local aliases internal to the subcircuit
definition for the node names used on the \texttt{X} instance lines.
Internal nodes are nodes inside the subcircuit definition that are
strictly local to that subcircuit.  Inside a subcircuit, these node
names may be used without restriction in device instance lines and
expressions on \texttt{B} source lines.

There are some circumstances when it is desirable to access internal
nodes of a subcircuit from outside that subcircuit.  \Xyce{} provides a
syntax that allows this to be done in {\em some\/} contexts.  The
primary context in which this is supported is on \texttt{.PRINT}
lines, to allow the user to print out signals that are usually local
to a subcircuit.

The syntax used by \Xyce{} to refer to nodes within a subcircuit is to
prefix the name of the node with the full path of subcircuit instances
in which the node is contained, with colons (:) separating the
instance names.  So, to reference a node ``A'' that is inside a
subcircuit instance called ``Xnot1'' inside another subcircuit
instance called ``Xmain'', one would refer to ``Xmain:Xnot1:A''

The same syntax works on \texttt{.PRINT} lines even if the subcircuit
node is one of the interface nodes on the \texttt{.SUBCKT} line, but
those nodes can also be accessed by using the names of the nodes at
the higher level of circuit hierarchy that are used on its instance
line.

\begin{centering}
\shadowbox{
\begin{minipage}{0.8\textwidth}
\begin{vquote}
\color{blue}* Netlist file demonstrating subcircuit node access\color{black}
V1  1   0   1
X1  1   2   demosubc
X2  2   0   demosubc
.subckt demosubc A B
R1 A C 1
R2 C B 1
.ends

.dc V1 1 5 1

*V(X1:A) and V(1) are the same signal.
*V(X1:C) is the internal C node of the X1 instance
*V(X2:C) is the internal C node of the X2 instance
*V(X1:B), V(X2:A) and V(2) are the same signal
.print DC V(X1:C) V(X2:C) V(X1:A) V(1)  V(X1:B) V(X2:A) V(2)
.end
\end{vquote}
\end{minipage}
}
\end{centering}

Subcircuit nodes may also be accessed from outside of the subcircuit
in \texttt{B} source voltage or current expressions, though this usage
violates the strict hierarchy of the netlist.  The one difference
between this usage and \texttt{.PRINT} usage is that it is not
possible to use the subcircuit node syntax to access interface nodes.
These must be accessed using the node names being used on the instance
line, as in the ``V(1)'' example in the netlist fragment above.

%%
%% Legal and illegal characters in device names and node names
%%
\subsection{Legal Characters in Node and Device Names}
\label{legalCharacters}
\index{legal characters} \index{illegal characters}
\Xyce{} node names and device names can consist of any printable ASCII
characters, with the following exceptions and caveats which may be
different than other SPICE-like circuit simulators.  The exceptions are:
\begin{XyceItemize}
\item White space (space, tab, newline) is not allowed.
\item Parentheses (``('' or ``)''), braces (``\{'' or ``\}''), commas,
colons, semi-colons, double quotes and single quotes are also not
allowed, since they do not work correctly in node names or device names
in all netlist contexts in \Xyce{}.
\end{XyceItemize}
The caveats are as follows:
\begin{XyceItemize}
\item The star (*) and question mark (?) characters are allowed in both
node names and device names.  However, those two characters also function
as ``print wildcards'' in \Xyce{}, per section~\ref{Print_Wildcards}.
So, that usage is discouraged.
\item Global nodes in \Xyce{} begin with the two characters ``\$G''.
\item The node named \texttt{0} (``zero'') is a special global node,
which is always the ground node.
\item These arithmetic operators \verb|%| \verb|^| \verb|&| \verb|?| \verb|:|
\verb|~| \verb|*| \verb|-| \verb|+| \verb|<| \verb|>| \verb|/|
\verb+|+ should not be used in node or device names that will
be used outside of a \Xyce{} ``operator'', such as \texttt{V()}, within
a \Xyce{} expresson.  Examples of this caveat are given below.
\item The \verb|#| character should not be used as the first character
of a node name that will be used within an expression.  Examples of this
caveat are also given below.
\end{XyceItemize}
These are some examples of the caveats of the use of arithmetic operators
and \verb|#| character within expressions:
\begin{verbatim}
* Okay since the + in the node name is enclosed within the V() operator.
.PRINT TRAN {V(1+) - V(+)}
* Okay since the R+ and R- device names are enclosed within the I() operator.
.PRINT TRAN {I(R+) * I(R-)}
* Okay, for printing the resistance value, since the R-1 device name
* is not used in an expression.
.PRINT TRAN R-1:R
* Will produce a parsing error, since the R-1 device name is used outside
* of an operator.  That makes this statement ambiguous within an expression.
.PRINT TRAN {R-1:R}
* These uses of # are okay.
.PRINT TRAN V(#) {V(1#) -1}
* These usages of # are parsing errors, since # is the first character
* in the node names.
.PRINT TRAN {V(#) - 2} {V(#1) -1}
\end{verbatim}

%%
%% Lead Current and Power Calculations
%%
\subsection{Lead Currents and Power Calculations}
\label{leadCurrentPowerCalculations}
\index{lead currents} \index{power calculations} For some devices,
such as independent voltage and current sources, the current through
that device is a ``solution'' variable.  For other devices, the
current through the device is a ``lead current'', whose value is
calculated during a post-processing step.  This approach has
ramifications in \Xyce{} for the availability and accuracy of lead
current values.  In particular, both lead currents and power
calculations need to have been explicitly enabled for a given device,
analysis type (e.g., \texttt{.AC}) or netlist command (e.g.,
\texttt{.MEASURE}).

For voltage sources, both V and I are solution variables.  So, their
accuracy is more likely to be limited by the nonlinear solver
tolerances (\texttt{RELTOL} and \texttt{ABSTOL}).  The lead current
accuracy, for a device like the resistor, can also be limited by the
right-hand side tolerance \texttt{RHSTOL}.  So, the calculated lead
currents through very small resistances (e.g., 1e-12) may be
inaccurate if the default solver tolerances for \Xyce{} are used.

Lead currents have the following additional limitations:
\begin{XyceItemize}
\item They are not enabled for \texttt{.AC} analyses.
\item They are not allowed in the expression controlling a B-Source.
\item They do not work for \texttt{.RESULT} statements.
\end{XyceItemize}

Lead currents and power calculations are available in
\texttt{.MEASURE} and \texttt{.FOUR} statements.

At this time the power calculations are only supported for {\tt .DC}
and {\tt .TRAN} analysis types and for a limited set of devices. In
addition, the results for semiconductor devices (D, J, M, Q and Z
devices) and the lossless transmission device (T device) may differ
from other simulators.  Consult the Features Supported by Xyce Device
Models table in section \ref{Analog_Devices} and the individual
sections on each device for more details.

As an example, the power supplied or dissipated by the voltage source
{\tt V} is calculated as $I \cdot \Delta V$ where the voltage drop is
calculated as $(V_+ - V_-)$ and positive current flows from $V_+$ to
$V_-$.  Dissipated power has a positive sign, while supplied power has
a negative sign.

An important note is that the power calculations are also a
post-processing step, which places a limit on the accuracy of
circuit-wide ``energy conservation'' calculations (e.g., total power
supplied by sources - total power dissipated in non-source devices) in
\Xyce{}.  The accuracy of the inputs ({\tt V} and {\tt I}) to the
power calculations is limited by the nonlinear solver and right-hand
side tolerances, as noted above, and the error in the power
calculations is upper-bounded by the sum of the product-terms of {\tt
  V*(error in I)} and {\tt I*(error in V)}.


%%
%% Capacitor
%%
\clearpage
\subsection{Capacitor}
\index{device!capacitor} \index{capacitor}
\input{C_Device}

%%
%% Inductor
%%
\clearpage
\subsection{Inductor}
\index{device!inductor} \index{inductor}
\input{L_Device}

%%
%% Mutual Inductors
%%
\clearpage
\subsection{Mutual Inductors}
\label{MutualInductor}
\index{device!mutualinductor} \index{mutualinductor}
\input{K_Device}

%%
%% Resistor
%%
\clearpage
\subsection{Resistor}
\index{device!resistor} \index{resistor}
\input{R_Device}

%%
%% Diode
%%
\clearpage
\subsection{Diode}
\index{device!diode} \index{diode}
\input{D_Device}

%%
%% Independent Current Source
%%
\clearpage
\subsection{Independent Current Source}
\index{device!independent voltage source} \index{independent voltage source}
\index{current source!independent}
\label{IndependentCurrentSource}
\input{I_Device}

%%
%% Independent Voltage Source
%%
\clearpage
\subsection{Independent Voltage Source}
\index{device!independent voltage source} \index{independent voltage source}
\index{voltage source!independent}
\input{V_Device}

%%
%% Voltage-Controlled Voltage-Source Section
%%

%%
%% Port device 
%%
\clearpage
\subsection{Port Device}
\index{device!port device} \index{port device}
\input{P_Device}

\clearpage
\subsection{Voltage Controlled Voltage Source}
\index{device!voltage controlled voltage source} \index{voltage controlled voltage source}
\index{voltage source!voltage controlled}
\input{E_Device}

%%
%% Current-Controlled Current-Source Section
%%
\clearpage
\subsection{Current Controlled Current Source}
\index{device!current controlled current source} \index{current controlled current source}
\index{current source!current controlled}
\input{F_Device}

%%
%% Voltage-Controlled Current-Source Section
%%
\clearpage
\subsection{Voltage Controlled Current Source}
\index{device!voltage controlled current source} \index{voltage controlled current source}
\index{current source!voltage controlled}
\input{G_Device}

%%
%% Current-Controlled Voltage-Source Section
%%
\clearpage
\subsection{Current Controlled Voltage Source}
\index{device!current controlled voltage source} \index{current controlled voltage source}
\index{voltage source!current controlled}
\input{H_Device}

%%
%% BSource Section
%%
\clearpage
\subsection{Nonlinear Dependent Source}
\label{B_Source_Device}
\index{device!bsource} \index{bsource}
\index{voltage source!nonlinear dependent} \index{current source!nonlinear dependent}
\input{B_Device}

%%
%% BJT Section
%%
\clearpage
\subsection{Bipolar Junction Transistor (BJT)}
\index{device!BJT} \index{BJT}
\input{Q_Device}

%%
%% JFET Section
%%
\clearpage
\subsection{Junction Field-Effect Transistor (JFET)}
\index{device!JFET} \index{JFET}
\input{J_Device}

%%
%% MESFET Section
%%
\clearpage
\subsection{Metal-Semiconductor FET (MESFET)}
\index{device!MESFET} \index{MESFET}
\input {Z_Device}

%%
%% MOSFET Subsection
%%
\clearpage
\subsection{MOS Field Effect Transistor (MOSFET)}
\index{device!MOSFET} \index{MOSFET}
\input{M_Device}

%%
%% Lossy Transmission Line Model (LTRA)
%%
\clearpage
\subsection{Lossy Transmission Line (LTRA)}
\index{device!ltra} \index{lossy transmission line}
\index{device!transmission line!lossy}
\input{O_Device}

%%
%% Voltage- or Current-controlled Switch Subsection
%%
\clearpage
\subsection{Voltage- or Current-controlled Switch}
\index{device!controlled switch} \index{controlled switch}
\input{S_Device}

%%
%% Generic Switch Subsection
%%
\clearpage
\subsection{Generic Switch}
\index{device!generic switch} \index{generic switch}
\input{SW_Device}

%%
%% YLIN device Subsection
%%
\clearpage
\subsection{Linear device}
\index{linear device}
\input{YLIN_Device}

%%
%% Lossless, Ideal Transmission Line Subsection
%%
\clearpage
\subsection{Lossless (Ideal) Transmission Line}
\index{device!lossless transmission line} \index{lossless transmission line}
\index{device!transmission line!lossless}
\input{T_Device}

%%
%% Lumped Transmission Line Subsection
%%
\clearpage
\subsection{Lumped Transmission Line}
\index{device!lumped transmission line} \index{lumped transmission line}
\index{device!transmission line!lumped}
\input{Transline_Device}

%%
%% Delay device Subsection
%%
\clearpage
\subsection{Ideal Delay}
\index{device!delay device}
\index{device!ideal delay device}
\input{Delay_Device}
%%
%% U Type Digital Device
%%
\clearpage
\subsection{Behavioral Digital Devices}
\index{device!digital devices} \index{digital devices}
\input{U_Device}

%%
%% Behavioral Digital Devices - Y Type now deprecated
%%
\clearpage
\subsection{Y-Type Behavioral Digital Devices (Deprecated)}
\index{device!digital devices, Y type} \index{Y type digital devices}
\input{DIGITAL_Device}

%%
%% YACC device Subsection
%%
\clearpage
\subsection{Accelerated mass}
\index{accelerated mass device}
\input{ACC_Device}

%%
%% Power Grid device Subsection
\clearpage
\subsection{Power Grid}
\index{power grid}
\input{Power_Grid_Device}

%%
%% Anti-Windup Limiter device Subsection
%\clearpage
%\subsection{Anti-Windup Limiter}
%\index{anti-windup limiter}
%\input{Anti_Windup_Limiter_Device}

%%
%% Memristor Device subsection
%%
\clearpage
\subsection{Memristor Device}
\index{memristor}
\input{MemristorTEAM}
\input{MemristorYakopcic}
\input{MemristorPEM}

%%
%% Subcircuit Subsection
%%
\clearpage
\subsection{Subcircuit}
\label{SubcircuitInstance}
\index{subcircuit}
\input{X_Device}

%%

%%% Local Variables:
%%% mode: latex
%%% End:

% END of Xyce_RG_app1.tex ************
